---
title: "Covid-19 Food Systems Database Analysis"
author: "Robert Berry"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 4
    smooth_scroll: yes
    theme: united
    code_folding: hide
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

The aim of this website is to report the ongoing analysis of the CCRI's [COVID-19 and Food Systems Database](http://www.ccri.ac.uk/covid19-food-db/). The current analysis is based on a version of the database downloaded on **14/01/2021**.

All of the tables and plots shown on this website can be accessed as individual files [HERE](https://connectglosac-my.sharepoint.com/:f:/g/personal/s2111547_glos_ac_uk/Et1CEJKr6lNDixyBZv6ApQcB32CNUmTerHOikgHynM9_-Q?e=dX3AU8)

<!-- ```{r setup, include=FALSE} -->
<!-- knitr::opts_chunk$set(echo = TRUE) -->

<!-- ``` -->

## 1. Data import and cleaning

Load data and prepare for analysis:

 - Trim white space on import <br />
 - Rename columns <br />
 - Reformat date column (convert from DD/MM/YY to  YY/MM/DD) <br />
 - Remove empty records <br />
 - Remove duplicate records <br />
 - Sort by date (descending) <br />
 - Add unique ID column
 - Correct ampersand import format
 
```{r echo=TRUE, eval=TRUE}
#> 1.1 Load libraries 
library(tidyverse) # Data muncging and analysis
library(here) # relative path management for reproducibility
library(lubridate) # for date string manipulation/conversion
library(janitor) # data cleaning functions
library(knitr) # report rendering with rmarkdown
library(ggplot2) # plots and visualisations

  
#> 1.2 Import data (trimming white space in the process)
db <- read_csv(here("In", "C19_Food_DB_220114.csv"), trim_ws = TRUE)
```

Table 1.1 Original database ("db") on import - **`r toString(nrow(db))`** records
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#> Glimpse
glimpse(db)
```

```{r echo=TRUE, eval=TRUE}
#> 1.3 Prep for analysis (clean, tidy, transform)
#> Rename columns
db <- db |> 
  rename(AUTH_SOURCE = `Author(s) / Source`, TYPE = `Article Type`, THEME_MAIN=`Theme(s)`, THEME_SUB = `Sub-Theme(s)`) 
for( i in colnames(db)){
    colnames(db)[which(colnames(db)==i)] = toupper(i)
}
#> Remove i
rm(i)
#> Convert date format to YYYY/MM/DD for analysis and sorting by date 
db$DATE <- as.Date(lubridate::parse_date_time(db$DATE, c('dmy', 'ymd')))

#> Remove empty records where all columns are "NA"
# Following filters rows with at least one column not "NA"
db <- janitor::remove_empty(db, which = "rows")

#> Remove duplicates
db <- db |> distinct()

# Add unique ID column
# First sort by date (oldest first)
db <- db |> 
  arrange(DATE)
# Add ID col
db$UID <- seq.int(nrow(db))
# Bring new UID column to front
db <- db |> select(UID, everything())

#> replace ampersand string "&amp;" with "&" in selected columns
db$THEME_MAIN <- (gsub("&amp;", "&", db$THEME_MAIN))
db$THEME_SUB <- (gsub("&amp;", "&", db$THEME_SUB))

#> Export as CSV
write_csv(db, here("Out", "Descriptive_Stats", "1_Current_Database_Cleaned", paste0("C19_Food_DB_Cleaned_", Sys.Date(), ".csv")))

```
Table 1.2 Processed database after cleaning and pre-processing**`r toString(nrow(db))`** records
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#> Glimpse
glimpse(db)
```
*(**Note 20/01/21** - requires further processing - e.g. new cols for shortened theme names)*
<br /> <br />



## 2. Themes: Count

This section includes tables and plots showing the summary counts of main themes and sub-themes in the database. 

### 2.1 Main Themes
This section shows the summary counts for main themes. <br /> <br />
**Note:** a small number of database entries have been allocated multiple main themes (see bottom of table). **Damian** - these can be left as is, or split and counted as single themes - let me know. <br /> <br />
**Also** - note that very long theme names affect the format of tables and plots - we need an alternative set of concise theme names for both main and sub-themes to improve presentation (task for DM and SR).

```{r echo=TRUE, eval=TRUE, fig.height = 6, fig.width = 9}
#> Group and count main themes
t2.1.theme.m.sum <- db |> 
  select(THEME_MAIN) |> 
  group_by(THEME_MAIN) |> 
  summarise(Count = n()) |> 
  arrange(desc(Count))
#> Render table on web page
knitr::kable(t2.1.theme.m.sum, col.names = c("Main theme", "Article count"), caption = "Table 2.1.1 Article count by main theme")
#> Export table as CSV file
write_csv(t2.1.theme.m.sum, here("Out", "Descriptive_Stats", "2_Themes_Count", "2.1_Main_Themes", "Table2.1_THEMES_MAIN_Count.csv"))
#> Create (and export) bar plot
p2.1 <- ggplot(t2.1.theme.m.sum, aes(x = reorder(THEME_MAIN, Count), y = Count)) +
  theme_bw() +
  ggtitle("Figure 2.1.1 Article count by main theme") +
  geom_bar(stat = "identity", fill = "#9e66ab") +
  theme(axis.title.y = element_blank()) +
  coord_flip() 
p2.1
ggsave(here("Out", "Descriptive_Stats", "2_Themes_Count", "2.1_Main_Themes", "Plot2.1_THEMES_MAIN_Count.png"), width = 9, height = 6)
  

```


### 2.2 Sub-Themes

This section shows the summary counts for sub-themes.

```{r echo=TRUE, eval=TRUE,results='asis', fig.height = 6, fig.width = 9}


#> Create list of main themes for iteration
t2.2_theme.m <- t2.1.theme.m.sum |> 
  slice(1:19) 
themes <- as.list(t2.2_theme.m$THEME_MAIN)
#> Sequential integer counter for figure numbers
i <-0 
#> Initiate loop
for(theme.m in themes){
#> Loop counter (for table caption number)
i <- i+1

#> Create data table (count of articles by sub-theme per main theme)
t2.2_loop <- db |>
 select(THEME_MAIN, THEME_SUB) |>
 filter(THEME_MAIN == theme.m) |>
 group_by(THEME_MAIN, THEME_SUB) |>
 summarise(Count = n()) |> 
 ungroup() |> 
 select(THEME_SUB, Count) |>
 arrange(desc(Count)) 
#> Remove main theme from THEME_SUB string (i.e. all text before and included hyphen)
t2.2_loop$THEME_SUB <- gsub("^.*?\\-","", t2.2_loop$THEME_SUB)
#> Trim WS
t2.2_loop$THEME_SUB <- trimws(t2.2_loop$THEME_SUB)

print(knitr::kable(t2.2_loop, col.names = c("Sub-theme", "Article count"), caption = paste0("Table 2.2.", i , ": ", theme.m)))
#> Add line break
cat("\n")
cat("\n")
cat("\n")


#> Export table as CSV file
write_csv(t2.2_loop, here("Out", "Descriptive_Stats", "2_Themes_Count", "2.2_Sub_Themes", paste0("Table 2.2.", i, "_", "_SUB_THEMES_Count.csv")))
#> Create (and export) bar plot
p2.2 <- ggplot(t2.2_loop, aes(x = reorder(THEME_SUB, Count), y = Count)) +
  theme_bw() +
  ggtitle(paste0("Figure 2.2.", i , ": ", theme.m)) +
  geom_bar(stat = "identity", fill = 	"#599ad3") +
  theme(axis.title.y = element_blank()) +
  theme(legend.position="none") +
  coord_flip()

#> Render on web page
print(p2.2)
#> Export plots
ggsave(here("Out", "Descriptive_Stats", "2_Themes_Count", "2.2_Sub_Themes", paste0("Figure_2.2.", i, "_", ".png")), width = 9, height = 6)

#> End loop
}

```

```{r}

#> Remove unwanted variables
rm(i)
```
<br />
<br />




## 3. Themes: Temporal analysis

In this section article occurrences are plotted over time by main theme. The pink rectanges in each plot indicate the time periods of the main Covid lockdowns in England (source: [**HERE**](https://www.instituteforgovernment.org.uk/charts/uk-government-coronavirus-lockdowns))



### 3.1 Main Themes

```{r echo=TRUE, eval=TRUE,results='asis', fig.height = 6, fig.width = 9}

#> Data frame to hold date ranges for lockdows
#> See: https://stackoverflow.com/questions/61479286/how-to-annotate-time-periods-on-line-plots-with-date-axis
Lockdowns <- data.frame(date_start= as_date(c("2020-03-23", "2020-11-05", "2021-01-06")),
                        date_end = as_date(c("2020-05-10","2020-12-02", "2021-03-08")))

#> Sequential integer counter for figure numbers
i <-0 
#> Initiate loop
for(theme.m in themes){
#> Loop counter (for table caption number)
i <- i+1

#> Non loop version
#> Get a data frame for one main theme just with ID and dates
#> Aggregate by week
#< Tip from: https://stackoverflow.com/questions/47503159/ggplot-using-grouped-date-variables-such-as-year-month
t3.1_theme.m.t <- db |> 
  select(UID, THEME_MAIN, DATE) |>  
  filter(THEME_MAIN == theme.m) |> 
  mutate(OBS = 1) |> 
  mutate(Month = floor_date(DATE, unit = "month")) |> 
  group_by(Month) |> 
  summarise(Count = sum(OBS))
#> Get maximum value of Count for use in plotting
max_val <- max(t3.1_theme.m.t$Count)

#> Plot
p3.1 <- ggplot()+
  theme_bw() +
  ggtitle(paste0("Figure 3.1.", i , ": ", theme.m)) +
  geom_rect(data = Lockdowns, aes(xmin = date_start, xmax = date_end, ymin = -Inf, ymax = Inf),
            fill = "red", alpha= 0.3) +
  geom_line(data = t3.1_theme.m.t, aes(x=Month, y=Count), size = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(NULL, date_labels = "%b %y", date_breaks = "2 months") +
  scale_y_continuous(breaks = seq(0, max_val, by = 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
p3.1

#> Render on web page
print(p3.1)

#> Export plots
ggsave(here("Out", "Descriptive_Stats", "3_Themes_Temporal", "3.1_Main_Themes_Plots", paste0("Figure_3.1.", i, "_", ".png")), width = 9, height = 6)

#> Add line break
cat("\n")
cat("\n")
cat("\n")
# #> Export plots
# ggsave(here("Out", "Descriptive_Stats", "2_Themes", "2.2_Sub_Themes", paste0("Table 2.2.", i, ".png")), width = 9, height = 6)

#> End loop
}
```



## 4. Keywords: Count

Summary count of keywords in the database. 

```{r echo=TRUE, eval=TRUE,results='asis', fig.height = 6, fig.width = 9}
#> Split keyword string and create long format table - i.e. 1 keyword per row
t4.1.kwords <- db |> 
  mutate(Keyword = strsplit(as.character(KEYWORDS), ",")) |> 
  unnest(Keyword)
#> Trim white space
t4.1.kwords$Keyword <- trimws(t4.1.kwords$Keyword)
#> Remove duplicates and recount
t4.1.kwords.count <- t4.1.kwords |> 
  group_by(Keyword) |> 
  summarise(Count = n()) |> 
  arrange(desc(Count))
#> Render table on web page
knitr::kable(t4.1.kwords.count, col.names = c("Keyword", "Count"), caption = "Table 4.1 Keyword count")
#> Export table as CSV file
write_csv(t4.1.kwords.count, here("Out", "Descriptive_Stats", "4_Keywords_Count", "Tables", "Table4.1_Keywords_Count.csv"))


```

## 5. Keywords: Temporal analysis

Analysis of keyword frequency plotted over time, with periods of lockdown shown. The top 20 most frequently occurring keywords are shown (this can be easily extended to more or all keywords)

```{r echo=TRUE, eval=TRUE,results='asis', fig.height = 6, fig.width = 9}

#> Get the 20 most frequently ocurring keywords
t5.1.kwords.top20 <- t4.1.kwords.count |> 
slice_max(Count, n = 20) |> 
# drop unwanted Count column
select(Keyword)

#> Merge with main keywords table to extract top 20
t5.1.kwords.plot <- merge(t4.1.kwords, t5.1.kwords.top20, by = "Keyword")

#> Get list of top 20 keywords for loop
kwords <- as.list(t5.1.kwords.top20$Keyword)

#> Sequential integer counter for figure numbers
i <-0 
#> Initiate loop
for(kword in kwords){
#> Loop counter (for table caption number)
i <- i+1

#> Create data table (count of articles by sub-theme per main theme)
t5.1_loop <- t4.1.kwords |>
 select(Keyword, DATE) |>
 filter(Keyword == kword) |> 
 mutate(OBS = 1) |> 
 mutate(Month = floor_date(DATE, unit = "month")) |> 
 group_by(Month) |> 
 summarise(Count = sum(OBS))

#> Get maximum value of Count for use in plotting
max_val <- max(t5.1_loop$Count)

#> Plot
p5.1 <- ggplot()+
  theme_bw() +
  ggtitle(paste0("Figure 5.", i , ": ", kword)) +
  geom_rect(data = Lockdowns, aes(xmin = date_start, xmax = date_end, ymin = -Inf, ymax = Inf),
            fill = "red", alpha= 0.3) +
  geom_line(data = t5.1_loop, aes(x=Month, y=Count), size = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(NULL, date_labels = "%b %y", date_breaks = "2 months") +
  scale_y_continuous(breaks = seq(0, max_val, by = 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
p5.1

#> Render on web page
print(p5.1)

#> Export plots
ggsave(here("Out", "Descriptive_Stats", "5_Keywords_Temporal", "Plots", paste0("Figure_5.", i, "_", kword, ".png")), width = 9, height = 6)


}

```


```{r}
#> Remove unwanted variables
rm(i)

```


## 6. Articles by type


```{r echo=TRUE, eval=TRUE, fig.height = 6, fig.width = 9}
#> Group and count article types
t6.1.article.sum <- db |> 
  select(TYPE) |> 
  group_by(TYPE) |> 
  summarise(Count = n()) |> 
  arrange(desc(Count))
#> Render table on web page
knitr::kable(t6.1.article.sum, col.names = c("Article Type", "Count"), caption = "Table 6.1 Article type (summary count)")
#> Export table as CSV file
write_csv(t6.1.article.sum, here("Out", "Descriptive_Stats", "6_Article_Type", "Table", "Table6.1_Article_Type_Count.csv"))
#> Create (and export) bar plot
p6.1 <- ggplot(t6.1.article.sum, aes(x = reorder(TYPE, Count), y = Count)) +
  theme_bw() +
  ggtitle("Figure 6.1 Article type") +
  geom_bar(stat = "identity", fill = "#d77fb3") +
  theme(axis.title.y = element_blank()) +
  coord_flip() 
p6.1
ggsave(here("Out", "Descriptive_Stats", "6_Article_Type", "Plot", "Plot6.1_Article_Type_Count.png"), width = 9, height = 6)
  

```

## **To do**

## 7. Topic modelling
Topic modelling of "summary" string variable


## 8. Topics: Temporal analysis
Plotting latent topics over time






