---
title: "Agricultural Transition: Great South West Partnership"
author: "Robert Berry"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 4
    smooth_scroll: yes
    theme: united
    code_folding: hide
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '4'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```
<br />
The aim of this website is to report the ongoing geospatial data analysis for the CCRI's Agricultural Transition: Great South West Partnership project. All of the tables and plots shown on this website can also be accessed as individual files [HERE](https://connectglosac.sharepoint.com/:f:/s/ccriprojects/EkmH8fOBINtNlhpJy_J-mqIBYQEk-p6fjgTJec68p_ji6A?e=hn0WaW). The full [R programming](https://www.r-project.org/about.html) code used to perform the work is included in this report, and can be accessed by clicking on the "Code" buttons. If you are unfamiliar with R code, comments (in plain English) have been added to describe the operation of each code block, so it should be possible to follow the methodology. 

<br />

## 1. Pillar 1: County-level

This section shows the code and outputs for the analysis of Pillar 1 (P1) payments at county level (for the counties of **Cornwall**, **Devon**, **Dorset**, and **Somerset**)

<br />

### 1.1 Data import & cleaning

Import and cleaning of the CAP Payments (data source: [HERE](https://cap-payments.defra.gov.uk/Search.aspx))  

**Step 1** - Load code packages and import data
 
```{r echo=TRUE, eval=TRUE}
#> 1.1.1 Load libraries 
library(tidyverse) # data munging and analysis
library(sf) # simple features for GIS
library(qgisprocess) # access to QGIS algorithms
library(here) # relative path management for reproducibility
library(lubridate) # for date string manipulation/conversion
library(janitor) # data cleaning functions
library(knitr) # report rendering with rmarkdown
library(ggplot2) # plots and visualisations
library(readxl) # import xls
library(scales) # for plot scale customisation
library(mapproj) # map zoom coords
library(leaflet) # interactive web maps
library(reshape2) # to reshape data (used for "melt" function)
library(units) # to convert from m2 to km2
  
#> 1.1.2 Import data (trimming white space)
#> "RPA" sheet
rpa.1 <- readxl::read_xlsx(here("In", "BPS_Glos", "2020_All_CAP_Search_Results_Data_P14.xlsx"), trim_ws = TRUE, sheet = "RPA")
#> "RPA2" sheet
rpa.2 <- readxl::read_xlsx(here("In", "BPS_Glos", "2020_All_CAP_Search_Results_Data_P14.xlsx"), trim_ws = TRUE, sheet = "RPA2")

```

**Step 2** - Data cleaning and pre-processing

```{r echo=TRUE, eval=TRUE}
#> 1.1.3 Data cleaning and pre-processing

#> Bind the two RPA tables together (they are split alphabetically by beneficiary name)
db <- rbind(rpa.1, rpa.2)

#> Remove duplicates
db <- db %>% 
  distinct()

#> Remove any empty records where all columns are "NA"
# Following filters rows with at least one column not "NA"
db <- janitor::remove_empty(db, which = "rows")

#> Select only relevant rcolumns
db <- db %>% 
  select("BeneficiaryCode", "PostcodePrefix_F202B", "TownCity_F202C", "Basic payment scheme", "Greening: practices beneficial for climate and environment") |> 
  arrange(desc(`Basic payment scheme`))


```


Table 1.1.1 Full database on import = *`r toString(nrow(db))`* records (all England)
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#> Glimpse
glimpse(db)
```

Table 1.1.2 First 6 rows of database
```{r echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#> Head
head(db)
```



<br />


### 1.2 Land cover processing

The CAP Payments dataset reports payments at postcode district level, but postcode districts do not conform to administrative boundaries (e.g. counties, district unitary authorities). Our approach is to calculate the area of agricultural land (using Corine land cover data) within each postcode district, and to use this to calculate the P1 payments. For districts which straddle county boundaries, the area of agricultural land both inside and outside of the target county are calculated, and the P1 payments are calculated based on the proportion of agricultural land inside the boundary. Agricultural land cover classes were extracted from the Corine 2018 land cover dataset and used for the agricultural area calculations. 

The following geospatial datasets are used for this analysis: <br />
 - County boundaries - [(OS BoundaryLine)](https://www.ordnancesurvey.co.uk/business-government/products/boundaryline) <br />
 - Postcode district areas - [(OpenDoor Postcode Districts)](https://www.opendoorlogistics.com/data/) <br />
 - Land Cover data - [(Corine 2018)](https://catalogue.ceh.ac.uk/documents/084e0bc6-e67f-4dad-9de6-0c698f60e34d) <br /> 
 
```{r echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, results='hide'}

#> Import county boundaries
#> Import ceremonial counties polygon layer from OS BoundaryLine dataset
counties.sw <- st_read(here("In", "Shape", "South_West.UPDATED.3.shp"), quiet = TRUE)

# glimpse(counties.sw)

#> Remove the deleted Bath and NE Somerset polygon (result of pre-geoprocessing in QGIS)
counties.sw <- counties.sw |> 
  filter(is.na(NAME_2))

#> Import postcode district boundary polygon data (source: https://www.opendoorlogistics.com/downloads/)
pcodes.gb <- st_read(here("In", "Shape", "Pcode_Districts_OpenDoor_2017.shp"), quiet = TRUE)

#> Import CORINE 2018 land cover data (polygons)
#> Data source: https://catalogue.ceh.ac.uk/documents/084e0bc6-e67f-4dad-9de6-0c698f60e34d
corine.gb <- st_read(here("In", "Shape", "corine_2018_GB.shp"), quiet = TRUE)
#> Select only agri land classes:
# 211 - Non-irrigated arable land
# 212 - Permanently irrigated land
# 213 - Rice fields
# 221 - Vineyards
# 222 - Fruit trees and berry plantations
# 223 - Olive groves
# 231 - Pastures
# 241 - Annual crops associated with permanent crops
# 242 - Complex cultivation patterns
# 243 - Land principally occupied by agriculture with significant areas of natural vegetation
# 244 - Agro-forestry areas
# 321 - Natural grasslands
# 322 - Moors and heathland
# 412 - Peatbogs
agri.land.classes <- c("211", "212", "213", "221", "222", "223", "231", "241", "242", "243", "244", "321", "322", "412")
#> Subset data based on land cover codes
corine.agri <- corine.gb |> 
  select(ID, CODE_18) |> 
  filter(CODE_18 %in% agri.land.classes)




  
#> Export agri data for detailed visual checking in QGIS
#> Remove previous shapefile export
unlink(here("Out", "Tests", "Corine_Agri.shp"))
unlink(here("Out", "Tests", "Corine_Agri.dbf"))
unlink(here("Out", "Tests", "Corine_Agri.prj"))
unlink(here("Out", "Tests", "Corine_Agri.shx"))
st_write(corine.agri, here("Out", "Tests", "Corine_Agri.shp"), quiet = TRUE)

#> Show an example plot of agri land extracted from Corine
#> Get Cornwall boundaries
cornwall.sf <- counties.sw |>
  filter(NAME == "Cornwall")
#> Clip corine.gb to extent of Cornwall
corine.clip <- st_intersection(corine.agri,cornwall.sf)
# 
# #> Previous static map (superseded by Leaflet map)
# #> Plot
# plot0 <- ggplot(data = cornwall.sf) +
#   ggtitle("Agricultural land: Cornwall (extracted from Corine 2018)") +
#   # theme_bw() +
#   geom_sf() +
#   geom_sf(data = corine.clip, fill = "green")
# #> Render on web page
# print(plot0)

```



*Figure 1.2.1 Extent of agricultural land (derived from Corine 2018)*
```{r out.width='100%', echo=TRUE}

#> This code chunk produces an interactive leafelt map of the SW region with Corine agri land shown

#> Subset counties.gb, selecting only Cornwall (inc Isles of Scilly), Devon, Somerset, and Dorset
#> Will also use this string in Section 1.3 loop
#> Create filter string (get names first!)
counties <- c("Cornwall", "Devon", "Dorset", "Somerset")
#> Create sf object of 4 counties
south.west <- counties.sw |>
  filter(NAME %in% counties)
#> Import clipped (to SW region) dissolved layer of Corine agri
#> Pre-processed in QGIS and imported as process in R takes too long
corine.sw <- st_read(here("In", "Shape", "Corine.sw.clip.diss.simp.100.diss3.shp"), quiet = TRUE)
#> Convert layers to WGS84 for use with Leaflet
south.west <- st_transform(south.west, 4326)
corine.sw <- st_transform(corine.sw, 4326)
#> Create Leaflet map
leaflet() |>
  addPolygons(data = corine.sw, fillOpacity = 0.5, color = "green", stroke = FALSE) |>
  addPolygons(data = south.west, fillOpacity = 0, label = TRUE) |>
  addTiles()

```


### 1.3 Reduction calculations

With all the required input data in place, P1 payments at county level can now be computed. A brief overview of the workflow: <br />

- **Step 1**: Select the four target counties from the GB county data layer <br />
- **Step 2**: Initiate a programming loop based on the counties (i.e. same code block is run for each county in turn) <br />
- **Step 3**: Create a spatial layer of postcode districts that spatially intersect with the "active" county  <br />
- **Step 4**: Create a spatial layer of postcode districts clipped exactly to the extent of the "active" county  <br />
- **Step 5**: Create a spatial layer of postcode districts clipped exactly to the extent of the "active" county  <br />
- **Step 6**: Using the Corine data on agricultural land area (prepared in Section 1.2), calculate the agricultural land area totals for intersected postcode district polygons, and clipped postcode district polygons respectively. This gives us two values: 1) the total area of agricultural land in each postcode district, and; 2) the area of agricultural land in each postcode district that is *within* the active county  <br />
- **Step 7**: Using the agricultural land area proportions and the P1 reduction figures, calculate the "baseline" value for P1 in 2020 and following years with payments applied up to and including 2027 <br />
- **Step 8**: Display output tables and bar plots  <br />
- **Step 9**: Export output tables and bar plots to CCRI shared drive  <br />

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}
#> Create filter string (get names first!)
counties <- c("Cornwall", "Devon", "Dorset", "Somerset")

#> Sequential integer counter (for figure numbers)
i <-0 

#> Initiate loop
for(active_county in counties){
  
#> Loop counter (for table caption number)
i <- i+1

#> Select target county (this will be start of loop)
county <- counties.sw |> 
  filter(NAME == active_county)

#> Select postcode district areas that intersect with active county polygon
pcodes.int <- pcodes.gb[county,]
#> Add area (km2) column
pcodes.int$AreaM2 <- st_area(pcodes.int)
#> Convert from m2 to km2
pcodes.int$AREA_KM2_TOTAL <- pcodes.int$AreaM2 / 1000000
pcodes.int$AREA_KM2_TOTAL <- round(pcodes.int$AREA_KM2_TOTAL, digits = 3)
pcodes.int$AREA_KM2_TOTAL <- as.numeric(pcodes.int$AREA_KM2_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.int.shp"))
unlink(here("Out", "Tests", "pcodes.int.dbf"))
unlink(here("Out", "Tests", "pcodes.int.prj"))
unlink(here("Out", "Tests", "pcodes.int.shx"))
st_write(pcodes.int, here("Out", "Tests", "pcodes.int.shp"), quiet = TRUE)


#> Generate a layer of clipped (cookie cutter) postcodes using active county boundary
pcodes.clip <- st_intersection(pcodes.int, county)
#> Add area (km2) column
pcodes.clip$AreaM2 <- st_area(pcodes.clip)
#> Convert from m2 to km2
pcodes.clip$AREA_KM2_CLIP<- pcodes.clip$AreaM2 / 1000000
pcodes.clip$AREA_KM2_CLIP <- round(pcodes.clip$AREA_KM2_CLIP, digits = 3)
pcodes.clip$AREA_KM2_CLIP <- as.numeric(pcodes.clip$AREA_KM2_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.clip.shp"))
unlink(here("Out", "Tests", "pcodes.clip.dbf"))
unlink(here("Out", "Tests", "pcodes.clip.prj"))
unlink(here("Out", "Tests", "pcodes.clip.shx"))
st_write(pcodes.clip, here("Out", "Tests", "pcodes.clip.shp"), quiet = TRUE)


#> To calculate agri land differences for postcodes which straddle the boundary of target county...
#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target county polygon
#> 3. Calculate percentage difference between the TWO sets of area calculations to gove % of agri land in each pcode district polygon


#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
agri.int.total <- st_intersection(pcodes.int, corine.agri)
#> Calculate area of Corine agri land
agri.int.total$AREA_AGRI_TOTAL <- st_area(agri.int.total)
#> Convert from m2 to km2
agri.int.total$AREA_AGRI_TOTAL <- agri.int.total$AREA_AGRI_TOTAL / 1000000
agri.int.total$AREA_AGRI_TOTAL <- round(agri.int.total$AREA_AGRI_TOTAL, digits = 3)
agri.int.total$AREA_AGRI_TOTAL <- as.numeric(agri.int.total$AREA_AGRI_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.total.shp"))
unlink(here("Out", "Tests", "agri.int.total.dbf"))
unlink(here("Out", "Tests", "agri.int.total.prj"))
unlink(here("Out", "Tests", "agri.int.total.shx"))
st_write(agri.int.total, here("Out", "Tests", "agri.int.total.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.total) <- NULL
agri.int.total <- agri.int.total |> 
  select(name, AREA_AGRI_TOTAL) |> 
  group_by(name) |> 
  summarise(AGRI_TOTAL = sum(AREA_AGRI_TOTAL))


#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target county polygon
agri.int.clip <- st_intersection(pcodes.clip, corine.agri)
#> Calculate area of Corine agri land
agri.int.clip$AREA_AGRI_CLIP <- st_area(agri.int.clip)
#> Convert from m2 to km2
agri.int.clip$AREA_AGRI_CLIP <- agri.int.clip$AREA_AGRI_CLIP / 1000000
agri.int.clip$AREA_AGRI_CLIP <- round(agri.int.clip$AREA_AGRI_CLIP, digits = 3)
agri.int.clip$AREA_AGRI_CLIP <- as.numeric(agri.int.clip$AREA_AGRI_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.clip.shp"))
unlink(here("Out", "Tests", "agri.int.clip.dbf"))
unlink(here("Out", "Tests", "agri.int.clip.prj"))
unlink(here("Out", "Tests", "agri.int.clip.shx"))
st_write(agri.int.clip, here("Out", "Tests", "agri.int.clip.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.clip) <- NULL
agri.int.clip <- agri.int.clip |> 
  select(name, AREA_AGRI_CLIP) |> 
  group_by(name) |> 
  summarise(AGRI_CLIP = sum(AREA_AGRI_CLIP))


#> 3. Calculate percentage difference between the two sets of area calculations to gove % of agri land in each pcode district polygon
#> Merge the two data frames to show size of agri area within and outside target county
agri.merge <- merge(agri.int.total, agri.int.clip, by = "name", all.x = TRUE)
#> Round area calcs up to 1 decimal place (to negate effect of small amounts of agri land being lost when clipped)
agri.merge$AGRI_TOTAL <- round(agri.merge$AGRI_TOTAL, digits = 3)
agri.merge$AGRI_CLIP <- round(agri.merge$AGRI_CLIP, digits = 2)
#> Calculate percentage of agri land within target county 
agri.merge$PCENT_AGRI_LAND <- agri.merge$AGRI_CLIP/ agri.merge$AGRI_TOTAL
#> Round up
agri.merge$PCENT_AGRI_LAND <- round(agri.merge$PCENT_AGRI_LAND, digits = 3)



#> Extract postcode districts from the BPS source data ("db") which intersect with the active county polygon boundary
#> Do this via a merge between db and pcodes.int, keeping only matching records in a new data frame
#> Rename pcodes.in and drop geom
pcodes.active <- pcodes.int
st_geometry(pcodes.active) <- NULL
BPS.merge <- merge(db, pcodes.active, by.x = "PostcodePrefix_F202B", "name", all.x = FALSE)
#> Convert all NAs to zeros in data frame
BPS.merge[is.na(BPS.merge)] <- 0



#> BPS Calcs by year

#> 2020
#> Create table with baseline P1 (BPS + Greening) payments by postcode district for 2020 (no payments applied)
t1.2020 <- BPS.merge %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2020_Baseline = sum(`Basic payment scheme`) + sum(`Greening: practices beneficial for climate and environment`))
#> Check sum total of P1 for reference
sum.original.p1 <- sum(t1.2020$P1_2020_Baseline)
#> Merge with agri.merge data frame to append 2020 calcs and create new master table "t1"
t1 <- merge(t1.2020, agri.merge, by.x = "PostcodePrefix_F202B", by.y = "name")
#> #> Calculate P1 payment based on area of agri land within each postcode area
t1$P1_2020 <- t1$P1_2020_Baseline * t1$PCENT_AGRI_LAND
#> Round to 2 decimal places
t1$P1_2020 <- round(t1$P1_2020, digits = 2)



#> 2021
t1.2021 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2021$P1_2020 <- t1.2021$`Basic payment scheme` + t1.2021$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2021 payments
t1.2021 <- t1.2021 %>% 
  mutate(P1_2021 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.95,
                              (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.90,
                              (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.80,
                              P1_2020 > 150000 ~ P1_2020 * 0.75))
# Group by postcode an summarise
t1.2021 <- t1.2021 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2021 = sum(P1_2021))
#> Round
t1.2021$P1_2021 <- round(t1.2021$P1_2021, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2021, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2021 <- t1$P1_2021 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2021 <- round(t1$P1_2021, digits = 2)
#> Check sum
sum.p1.2021 <- sum(t1$P1_2021)



#> 2022
t1.2022 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2022$P1_2020 <- t1.2022$`Basic payment scheme` + t1.2022$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2022 payments
t1.2022 <- t1.2022 %>% 
   mutate(P1_2022 = case_when(P1_2020<=30000 ~ P1_2020* 0.80,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.75,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.65,
                             P1_2020> 150000 ~ P1_2020* 0.60))
# Group by postcode an summarise
t1.2022 <- t1.2022 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2022 = sum(P1_2022))
#> Round
t1.2022$P1_2022 <- round(t1.2022$P1_2022, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2022, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2022 <- t1$P1_2022 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2022 <- round(t1$P1_2022, digits = 2)
#> Check sum
sum.p1.2022 <- sum(t1$P1_2022)


#> 2023
t1.2023 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2023$P1_2020 <- t1.2023$`Basic payment scheme` + t1.2023$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2023 payments
t1.2023 <- t1.2023 %>% 
  mutate(P1_2023 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.65,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.60,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.50,
                             P1_2020 > 150000 ~ P1_2020 * 0.45))
# Group by postcode an summarise
t1.2023 <- t1.2023 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2023 = sum(P1_2023))
#> Round
t1.2023$P1_2023 <- round(t1.2023$P1_2023, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2023, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2023 <- t1$P1_2023 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2023 <- round(t1$P1_2023, digits = 2)
#> Check sum
sum.p1.2023 <- sum(t1$P1_2023)


#> 2024
t1.2024 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2024$P1_2020 <- t1.2024$`Basic payment scheme` + t1.2024$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2024 payments
t1.2024 <- t1.2024 %>% 
  mutate(P1_2024 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.50,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.45,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.35,
                             P1_2020 > 150000 ~ P1_2020 * 0.30))
# Group by postcode an summarise
t1.2024 <- t1.2024 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2024 = sum(P1_2024))
#> Round
t1.2024$P1_2024 <- round(t1.2024$P1_2024, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2024, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2024 <- t1$P1_2024 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2024 <- round(t1$P1_2024, digits = 2)
#> Check sum
sum.p1.2024 <- sum(t1$P1_2024)


#> 2025
t1.2025 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2025$P1_2020 <- t1.2025$`Basic payment scheme` + t1.2025$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2025 payments
t1.2025 <- t1.2025 %>% 
 mutate(P1_2025 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.40,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.35,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.25,
                             P1_2020 > 150000 ~ P1_2020 * 0.20))
# Group by postcode an summarise
t1.2025 <- t1.2025 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2025 = sum(P1_2025))
#> Round
t1.2025$P1_2025 <- round(t1.2025$P1_2025, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2025, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2025 <- t1$P1_2025 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2025 <- round(t1$P1_2025, digits = 2)
#> Check sum
sum.p1.2025 <- sum(t1$P1_2025)


#> 2026
t1.2026 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2026$P1_2020 <- t1.2026$`Basic payment scheme` + t1.2026$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2026 payments
t1.2026 <- t1.2026 %>% 
  mutate(P1_2026 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.25,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.25,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.15,
                             P1_2020 > 150000 ~ P1_2020 * 0.15))
# Group by postcode an summarise
t1.2026 <- t1.2026 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2026 = sum(P1_2026))
#> Round
t1.2026$P1_2026 <- round(t1.2026$P1_2026, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2026, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2026 <- t1$P1_2026 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2026 <- round(t1$P1_2026, digits = 2)
#> Check sum
sum.p1.2026 <- sum(t1$P1_2026)


#> 2027
t1.2027 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2027$P1_2020 <- t1.2027$`Basic payment scheme` + t1.2027$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2027 payments
t1.2027 <- t1.2027 %>% 
   mutate(P1_2027 = case_when(P1_2020<=30000 ~ P1_2020* 0.15,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.15,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.10,
                             P1_2020> 150000 ~ P1_2020* 0.10))
# Group by postcode an summarise
t1.2027 <- t1.2027 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2027 = sum(P1_2027))
#> Round
t1.2027$P1_2027 <- round(t1.2027$P1_2027, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2027, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2027 <- t1$P1_2027 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2027 <- round(t1$P1_2027, digits = 2)
#> Check sum
sum.p1.2027 <- sum(t1$P1_2027)

#> Convert all NAs to zeros in data frame
t1[is.na(t1)] <- 0



#> Create plot

#> P1 payments by year
p1.in <- as.data.frame(colSums(t1[6:13]))
#> Change rownames to column "Value"
p1.plot <- tibble::rownames_to_column(p1.in, "VALUE")
#> Extract year from string
p1.plot$VALUE <- sub("^.*([0-9]{4}).*", "\\1", p1.plot$VALUE)
names(p1.plot)[1]<-paste("Year")
names(p1.plot)[2]<-paste("Value_bps")

#> Print table t1 on web page
print(knitr::kable(t1, col.names = c("PC", "2020_Unadjusted", "Agri_Total", "Agri_In", "Agri_PC", "2020", "2021", "2022", "2023", "2024", "2025", "2026", "2027"), caption = paste0("Table 1.", i , " ", "P1 payments by postcode district - ",  active_county)))

#> Add line breaks
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")


# Simple bar chart
plot1 <- ggplot(p1.plot, aes(x=Year, y=Value_bps)) + 
  theme_bw() +
  geom_bar(stat = "identity", fill="#2c66b8", width = 0.6) +
  geom_text(aes(label= paste0(round(Value_bps / 1000000, digits = 1), " M")), vjust = 1.5, colour = "white") +
  labs(title = paste0("Pillar 1 payments:", " ", active_county), x = "Year", y = "Value (£)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))
plot1

#> Add line breaks
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")

#> Render on web page
print(plot1)

#> Export the plot
ggsave(here("Out", "P1", "County", "Plot", paste0("P1_payments_", active_county, ".png")))

#> Export final t1 table
write_csv(t1, here("Out", "P1", "County", "CSV", paste0("P1_payments_", active_county, ".csv")))

}
          

```



### 1.4 Claimant numbers

<br />

Calculating the number of P1 claimants in each county (2020 RPA data)


```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}


#> Create filter string (get names first!)
counties <- c("Cornwall", "Devon", "Dorset", "Somerset")

#> Sequential integer counter (for figure numbers)
i <-0 

#> Initiate loop
for(active_county in counties){
  
#> Loop counter (for table caption number)
i <- i+1

#> Load reductions table for each county
p1.red.active <- read_csv(here("Out", "P1", "County", "CSV", paste0("P1_Reductions_", active_county, ".csv")))
p1.red.active  <- p1.red.active |> 
  rename(Pcode_District = PostcodePrefix_F202B)

#> From the above table, extract a postcode district lookup table for merging with raw RPA data
p1.pcodes <- p1.red.active |> 
  select(Pcode_District)

#> Merge with RPA data
p1.rpa <- merge(db, p1.pcodes, by.x = "PostcodePrefix_F202B",  by.y = "Pcode_District")
p1.rpa <- p1.rpa |> 
  rename(Pcode_District = PostcodePrefix_F202B)

#> Group by postcode and summarise (count of claimants)
p1.claims.sum <- p1.rpa |> 
  select(Pcode_District) |> 
  group_by(Pcode_District) |> 
  summarise(Claimants = n())
  

#> Merge back with reductions table for target count to obtain % agri land in pcode area for claimant estimation
p1.claims <- merge(p1.claims.sum, p1.red.active, by = "Pcode_District", all.x = TRUE)
p1.claims <- p1.claims |> 
  select(Pcode_District, Claimants, PCENT_AGRI_LAND) |> 
  mutate(Claimants_Est = Claimants * PCENT_AGRI_LAND)
p1.claims$Claimants_Est <- round(p1.claims$Claimants_Est, digits = 0)

#> Create summary table showing total number of claimants per county
p1.claims.total <- as.data.frame(sum(p1.claims$Claimants_Est))
p1.claims.total <- p1.claims.total |>
  rename(Total = `sum(p1.claims$Claimants_Est)`)

 
#> Print table on web page
print(knitr::kable(p1.claims, caption = paste0("Table 1.4.", i , " ", "No. of P1 claimants by postcode district - ",  active_county, " (TOTAL = ", p1.claims.total$Total, ")")))



#> Export table
write_csv(p1.claims, here("Out", "Claimants", "CSV", paste0("P1_Claimants_by_Pcode_District_", active_county, ".csv")))

#> Export totals table
write_csv(p1.claims.total, here("Out", "Claimants", "CSV", paste0("P1_Total_Claimants_", active_county, ".csv")))


}


```



<br />
<br />



## 2. Pillar 1: District-level

Calculation of P1 payment payments at sub-county (district unitary authority) level. Uses same basic methodology as above, but the level of data management complexity is higher due to multiple area-within-area p1 reduction calculations.

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Get district boundary data for SW counties
districts.sw <- st_read(here("In", "Shape", "Districts.SW.UPDATED.2.shp"), quiet = TRUE)
#> Convert Sw counties layer back to British National Grid
south.west <- st_transform(south.west, 27700)
#> Join districts with SW counties
districts.sw <- st_join(districts.sw, south.west, largest = TRUE) |> 
  filter(!is.na(NAME.y)) |> 
  select(NAME.x, NAME.y) |> 
  rename(NAME_DISTRICT = NAME.x, NAME_COUNTY = NAME.y) 

#? Remove string "(B)" from district names
# # districts.sw$NAME <- str_remove_all(districts.sw$NAME, "(B)")
districts.sw$NAME_DISTRICT <- gsub("\\s*\\([^\\)]+\\)", "", districts.sw$NAME_DISTRICT)
#> Trim WS
districts.sw$NAME_DISTRICT <- trimws(districts.sw$NAME_DISTRICT)
# head(districts.sw)

#> Create an empty data table to hold the P1 payments for districts - will be populated in below loop
district.summary <- data.frame(Name=character(),
                                P1_2020=as.numeric(),
                                P1_2021=as.numeric(),
                                P1_2022=as.numeric(), 
                                P1_2023=as.numeric(), 
                                P1_2024=as.numeric(), 
                                P1_2025=as.numeric(), 
                                P1_2026=as.numeric(), 
                                P1_2027=as.numeric())
                         


#> Sequential integer counter (for figure numbers)
i <-0

#> Initiate for loop
for(active_county in counties){

#> Loop counter (for table caption number)
i <- i+1


#> Initiate for loop here
#> For county in counties
target_county <- counties.sw |>
  filter(NAME == active_county)
head(target_county)


# #> Get the first county (example here without a loop = Cornwall)
# #> For county in counties
# target_county <- counties.gb |>
#   filter(NAME == "Cornwall")


#> Clip districts.sw to extent of counties (do for one county initially - Cornwall)
districts.clip <- st_intersection(districts.sw, target_county) |> 
#> Get only the districts that are officially within the active county
  #> (During the st_join process some slightly overlapping districts from other counties may be joined
  filter(NAME_COUNTY == active_county)

head(active_county)
head(districts.clip)

#> NEED TO START ANOTHER FOR LOOP HERE TO LOOP THROUGH DISTRICTS WITHIN COUNTY
#> FOR NOW CHOOSE ISLES OF SCILLY WITHOUT FOR LOOP
districts <- as.list(districts.clip$NAME_DISTRICT)

#> Initiate districts loop
for(district in districts){

active_district <- districts.clip |> 
  filter(NAME_DISTRICT == district)
head(active_district)

#> Select postcode district areas that intersect with active district polygon
pcodes.int <- pcodes.gb[active_district,]
head(pcodes.int)
#> Add area (km2) column
pcodes.int$AreaM2 <- st_area(pcodes.int)
#> Convert from m2 to km2
pcodes.int$AREA_KM2_TOTAL <- pcodes.int$AreaM2 / 1000000
pcodes.int$AREA_KM2_TOTAL <- round(pcodes.int$AREA_KM2_TOTAL, digits = 3)
pcodes.int$AREA_KM2_TOTAL <- as.numeric(pcodes.int$AREA_KM2_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.int.shp"))
unlink(here("Out", "Tests", "pcodes.int.dbf"))
unlink(here("Out", "Tests", "pcodes.int.prj"))
unlink(here("Out", "Tests", "pcodes.int.shx"))
st_write(pcodes.int, here("Out", "Tests", "pcodes.int.shp"), quiet = TRUE)


#> Generate a layer of clipped (cookie cutter) postcodes using active district boundary
pcodes.clip <- st_intersection(pcodes.int, active_district)
#> Add area (km2) column
pcodes.clip$AreaM2 <- st_area(pcodes.clip)
#> Convert from m2 to km2
pcodes.clip$AREA_KM2_CLIP<- pcodes.clip$AreaM2 / 1000000
pcodes.clip$AREA_KM2_CLIP <- round(pcodes.clip$AREA_KM2_CLIP, digits = 3)
pcodes.clip$AREA_KM2_CLIP <- as.numeric(pcodes.clip$AREA_KM2_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.clip.shp"))
unlink(here("Out", "Tests", "pcodes.clip.dbf"))
unlink(here("Out", "Tests", "pcodes.clip.prj"))
unlink(here("Out", "Tests", "pcodes.clip.shx"))
st_write(pcodes.clip, here("Out", "Tests", "pcodes.clip.shp"), quiet = TRUE)


#> To calculate agri land differences for postcodes which straddle the boundary of district...
#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target district polygon
#> 3. Calculate percentage difference between the TWO sets of area calculations to gove % of agri land in each pcode district polygon

#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
agri.int.total <- st_intersection(pcodes.int, corine.agri)
head(agri.int.total)
#> Calculate area of Corine agri land
agri.int.total$AREA_AGRI_TOTAL <- st_area(agri.int.total)
#> Convert from m2 to km2
agri.int.total$AREA_AGRI_TOTAL <- agri.int.total$AREA_AGRI_TOTAL / 1000000
agri.int.total$AREA_AGRI_TOTAL <- round(agri.int.total$AREA_AGRI_TOTAL, digits = 3)
agri.int.total$AREA_AGRI_TOTAL <- as.numeric(agri.int.total$AREA_AGRI_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.total.shp"))
unlink(here("Out", "Tests", "agri.int.total.dbf"))
unlink(here("Out", "Tests", "agri.int.total.prj"))
unlink(here("Out", "Tests", "agri.int.total.shx"))
st_write(agri.int.total, here("Out", "Tests", "agri.int.total.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.total) <- NULL
agri.int.total <- agri.int.total |> 
  select(name, AREA_AGRI_TOTAL) |> 
  group_by(name) |> 
  summarise(AGRI_TOTAL = sum(AREA_AGRI_TOTAL))
head(agri.int.total)



#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target district polygon
agri.int.clip <- st_intersection(pcodes.clip, corine.agri)
#> Calculate area of Corine agri land
agri.int.clip$AREA_AGRI_CLIP <- st_area(agri.int.clip)
#> Convert from m2 to km2
agri.int.clip$AREA_AGRI_CLIP <- agri.int.clip$AREA_AGRI_CLIP / 1000000
agri.int.clip$AREA_AGRI_CLIP <- round(agri.int.clip$AREA_AGRI_CLIP, digits = 3)
agri.int.clip$AREA_AGRI_CLIP <- as.numeric(agri.int.clip$AREA_AGRI_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.clip.shp"))
unlink(here("Out", "Tests", "agri.int.clip.dbf"))
unlink(here("Out", "Tests", "agri.int.clip.prj"))
unlink(here("Out", "Tests", "agri.int.clip.shx"))
st_write(agri.int.clip, here("Out", "Tests", "agri.int.clip.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.clip) <- NULL
agri.int.clip <- agri.int.clip |> 
  select(name, AREA_AGRI_CLIP) |> 
  group_by(name) |> 
  summarise(AGRI_CLIP = sum(AREA_AGRI_CLIP))


#> 3. Calculate percentage difference between the two sets of area calculations to gove % of agri land in each pcode district polygon
#> Merge the two data frames to show size of agri area within and outside target county
agri.merge <- merge(agri.int.total, agri.int.clip, by = "name", all.x = TRUE)
#> Round area calcs up to 1 decimal place (to negate effect of small amounts of agri land being lost when clipped)
agri.merge$AGRI_TOTAL <- round(agri.merge$AGRI_TOTAL, digits = 3)
agri.merge$AGRI_CLIP <- round(agri.merge$AGRI_CLIP, digits = 2)
#> Calculate percentage of agri land within target county 
agri.merge$PCENT_AGRI_LAND <- agri.merge$AGRI_CLIP/ agri.merge$AGRI_TOTAL
#> Round up
agri.merge$PCENT_AGRI_LAND <- round(agri.merge$PCENT_AGRI_LAND, digits = 3)
head(agri.merge)


#> Extract postcode districts from the BPS source data ("db") which intersect with the active county polygon boundary
#> Do this via a merge between db and pcodes.int, keeping only matching records in a new data frame
#> Rename pcodes.in and drop geom
pcodes.active <- pcodes.int
st_geometry(pcodes.active) <- NULL
BPS.merge <- merge(db, pcodes.active, by.x = "PostcodePrefix_F202B", "name", all.x = FALSE)
#> Convert all NAs to zeros in data frame
BPS.merge[is.na(BPS.merge)] <- 0
head(BPS.merge)


#> BPS Calcs by year (for target district)

#> 2020
#> Create table with baseline P1 (BPS + Greening) payments by postcode district for 2020 (no payments applied)
t1.2020 <- BPS.merge %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2020_Baseline = sum(`Basic payment scheme`) + sum(`Greening: practices beneficial for climate and environment`))
#> Check sum total of P1 for reference
sum.original.p1 <- sum(t1.2020$P1_2020_Baseline)
#> Merge with agri.merge data frame to append 2020 calcs and create new master table "t1"
t1 <- merge(t1.2020, agri.merge, by.x = "PostcodePrefix_F202B", by.y = "name")
#> #> Calculate P1 payment based on area of agri land within each postcode area
t1$P1_2020 <- t1$P1_2020_Baseline * t1$PCENT_AGRI_LAND
#> Round to 2 decimal places
t1$P1_2020 <- round(t1$P1_2020, digits = 2)




#> 2021
t1.2021 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2021$P1_2020 <- t1.2021$`Basic payment scheme` + t1.2021$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2021 payments
t1.2021 <- t1.2021 %>% 
  mutate(P1_2021 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.95,
                              (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.90,
                              (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.80,
                              P1_2020 > 150000 ~ P1_2020 * 0.75))
# Group by postcode an summarise
t1.2021 <- t1.2021 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2021 = sum(P1_2021))
#> Round
t1.2021$P1_2021 <- round(t1.2021$P1_2021, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2021, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2021 <- t1$P1_2021 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2021 <- round(t1$P1_2021, digits = 2)
#> Check sum
sum.p1.2021 <- sum(t1$P1_2021)



#> 2022
t1.2022 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2022$P1_2020 <- t1.2022$`Basic payment scheme` + t1.2022$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2022 payments
t1.2022 <- t1.2022 %>% 
   mutate(P1_2022 = case_when(P1_2020<=30000 ~ P1_2020* 0.80,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.75,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.65,
                             P1_2020> 150000 ~ P1_2020* 0.60))
# Group by postcode an summarise
t1.2022 <- t1.2022 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2022 = sum(P1_2022))
#> Round
t1.2022$P1_2022 <- round(t1.2022$P1_2022, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2022, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2022 <- t1$P1_2022 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2022 <- round(t1$P1_2022, digits = 2)
#> Check sum
sum.p1.2022 <- sum(t1$P1_2022)


#> 2023
t1.2023 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2023$P1_2020 <- t1.2023$`Basic payment scheme` + t1.2023$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2023 payments
t1.2023 <- t1.2023 %>% 
  mutate(P1_2023 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.65,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.60,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.50,
                             P1_2020 > 150000 ~ P1_2020 * 0.45))
# Group by postcode an summarise
t1.2023 <- t1.2023 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2023 = sum(P1_2023))
#> Round
t1.2023$P1_2023 <- round(t1.2023$P1_2023, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2023, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2023 <- t1$P1_2023 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2023 <- round(t1$P1_2023, digits = 2)
#> Check sum
sum.p1.2023 <- sum(t1$P1_2023)


#> 2024
t1.2024 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2024$P1_2020 <- t1.2024$`Basic payment scheme` + t1.2024$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2024 payments
t1.2024 <- t1.2024 %>% 
  mutate(P1_2024 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.50,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.45,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.35,
                             P1_2020 > 150000 ~ P1_2020 * 0.30))
# Group by postcode an summarise
t1.2024 <- t1.2024 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2024 = sum(P1_2024))
#> Round
t1.2024$P1_2024 <- round(t1.2024$P1_2024, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2024, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2024 <- t1$P1_2024 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2024 <- round(t1$P1_2024, digits = 2)
#> Check sum
sum.p1.2024 <- sum(t1$P1_2024)


#> 2025
t1.2025 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2025$P1_2020 <- t1.2025$`Basic payment scheme` + t1.2025$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2025 payments
t1.2025 <- t1.2025 %>% 
 mutate(P1_2025 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.40,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.35,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.25,
                             P1_2020 > 150000 ~ P1_2020 * 0.20))
# Group by postcode an summarise
t1.2025 <- t1.2025 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2025 = sum(P1_2025))
#> Round
t1.2025$P1_2025 <- round(t1.2025$P1_2025, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2025, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2025 <- t1$P1_2025 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2025 <- round(t1$P1_2025, digits = 2)
#> Check sum
sum.p1.2025 <- sum(t1$P1_2025)


#> 2026
t1.2026 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2026$P1_2020 <- t1.2026$`Basic payment scheme` + t1.2026$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2026 payments
t1.2026 <- t1.2026 %>% 
  mutate(P1_2026 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.25,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.25,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.15,
                             P1_2020 > 150000 ~ P1_2020 * 0.15))
# Group by postcode an summarise
t1.2026 <- t1.2026 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2026 = sum(P1_2026))
#> Round
t1.2026$P1_2026 <- round(t1.2026$P1_2026, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2026, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2026 <- t1$P1_2026 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2026 <- round(t1$P1_2026, digits = 2)
#> Check sum
sum.p1.2026 <- sum(t1$P1_2026)


#> 2027
t1.2027 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2027$P1_2020 <- t1.2027$`Basic payment scheme` + t1.2027$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2027 payments
t1.2027 <- t1.2027 %>% 
   mutate(P1_2027 = case_when(P1_2020<=30000 ~ P1_2020* 0.15,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.15,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.10,
                             P1_2020> 150000 ~ P1_2020* 0.10))
# Group by postcode an summarise
t1.2027 <- t1.2027 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2027 = sum(P1_2027))
#> Round
t1.2027$P1_2027 <- round(t1.2027$P1_2027, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2027, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2027 <- t1$P1_2027 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2027 <- round(t1$P1_2027, digits = 2)
#> Check sum
sum.p1.2027 <- sum(t1$P1_2027)

#> Convert all NAs to zeros in data frame
t1[is.na(t1)] <- 0

#> Create a new data frame to hold P1 reduction values by year summed for each district
head(active_district)
district.summary <- district.summary |> 
  add_row(Name = district, 
          P1_2020 = sum(t1$P1_2020),
          P1_2021 = sum(t1$P1_2021),
          P1_2022 = sum(t1$P1_2022),
          P1_2023 = sum(t1$P1_2023),
          P1_2024 = sum(t1$P1_2024),
          P1_2025 = sum(t1$P1_2025),
          P1_2026 = sum(t1$P1_2026),
          P1_2027 = sum(t1$P1_2027))
head(district.summary)
#> Wipe t1 rows clean
t1 <- t1[0,]



#> Web plot

}



#> Print table district.summary on web page
print(knitr::kable(district.summary, caption = paste0("Table 2.", i , " ", "P1 payments by district - ",  active_county)))

cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")

#> Create bar plots

#> Get a list of districts from the active district.summary table
districts.list <- as.list(district.summary$Name)

for (district.active in districts.list)

{

#> Create data table with only active row (district) from districts.summary table
df <- district.summary|> 
  filter(Name == district.active)
#> Shape data
p2.in <- as.data.frame(colSums(df[2:9]))
#> Change rownames to column "Value"
p2.plot <- tibble::rownames_to_column(p2.in, "VALUE")
#> Extract year from string
p2.plot$VALUE <- sub("^.*([0-9]{4}).*", "\\1", p2.plot$VALUE)
names(p2.plot)[1]<-paste("Year")
names(p2.plot)[2]<-paste("Value_bps")

# Simple bar chart
plot2 <- ggplot(p2.plot, aes(x=Year, y=Value_bps)) + 
  theme_bw() +
  geom_bar(stat = "identity", fill="#9e66ab", width = 0.6) +
  geom_text(aes(label= paste0(round(Value_bps / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white") +
  labs(title = paste0("Pillar 1 payments:", " ", district.active), x = "Year", y = "Value (£)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))
plot2
print(plot2)


#> Export the plot
ggsave(here("Out", "P1", "District", "Plot", paste0("P1_payments_", district.active, ".png")))


}



#> Export table
write_csv(district.summary, here("Out", "P1", "District", "CSV", paste0("P1_payments_", active_county, ".csv")))



#> Wipe district.summary rows clean
district.summary <- district.summary[0,]


  
}

```
<br />
<br />

## 3. Pillar 1: National Parks

Pillar one reduction analysis conducted for Exmoor and Dartmoor National Parks. National Parks boundary data from Natural England Geoportal. 


```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Import nat parks data
nat.parks <- st_read(here("In", "Shape", "Nat.Parks.SW.shp"), stringsAsFactors = FALSE, quiet = TRUE)
#> Change nat parks "NAME" to Capital case
nat.parks <- nat.parks |> 
  mutate(NAME = str_to_title(NAME, locale = "en"))
# glimpse(nat.parks)

#> Create filter string (get names first!)
nat.parks.list <- c("Exmoor", "Dartmoor")

#> Sequential integer counter (for figure numbers)
i <-0 

#> Initiate loop
for(active_park in nat.parks.list){
  
#> Loop counter (for table caption number)
i <- i+1

#> Select target county (this will be start of loop)
park <- nat.parks|> 
  filter(NAME == active_park)

#> Select postcode district areas that intersect with active county polygon
pcodes.int <- pcodes.gb[park,]
#> Add area (km2) column
pcodes.int$AreaM2 <- st_area(pcodes.int)
#> Convert from m2 to km2
pcodes.int$AREA_KM2_TOTAL <- pcodes.int$AreaM2 / 1000000
pcodes.int$AREA_KM2_TOTAL <- round(pcodes.int$AREA_KM2_TOTAL, digits = 3)
pcodes.int$AREA_KM2_TOTAL <- as.numeric(pcodes.int$AREA_KM2_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.int.shp"))
unlink(here("Out", "Tests", "pcodes.int.dbf"))
unlink(here("Out", "Tests", "pcodes.int.prj"))
unlink(here("Out", "Tests", "pcodes.int.shx"))
st_write(pcodes.int, here("Out", "Tests", "pcodes.int.shp"), quiet = TRUE)


#> Generate a layer of clipped (cookie cutter) postcodes using active county boundary
pcodes.clip <- st_intersection(pcodes.int, park)
#> Add area (km2) column
pcodes.clip$AreaM2 <- st_area(pcodes.clip)
#> Convert from m2 to km2
pcodes.clip$AREA_KM2_CLIP<- pcodes.clip$AreaM2 / 1000000
pcodes.clip$AREA_KM2_CLIP <- round(pcodes.clip$AREA_KM2_CLIP, digits = 3)
pcodes.clip$AREA_KM2_CLIP <- as.numeric(pcodes.clip$AREA_KM2_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "pcodes.clip.shp"))
unlink(here("Out", "Tests", "pcodes.clip.dbf"))
unlink(here("Out", "Tests", "pcodes.clip.prj"))
unlink(here("Out", "Tests", "pcodes.clip.shx"))
st_write(pcodes.clip, here("Out", "Tests", "pcodes.clip.shp"), quiet = TRUE)


#> To calculate agri land differences for postcodes which straddle the boundary of target county...
#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target county polygon
#> 3. Calculate percentage difference between the TWO sets of area calculations to gove % of agri land in each pcode district polygon


#> 1. Intersect pcodes.int with corine.agri, to calculate area of agri land for all intersecting pcode district polys (whole polygon)
agri.int.total <- st_intersection(pcodes.int, corine.agri)
#> Calculate area of Corine agri land
agri.int.total$AREA_AGRI_TOTAL <- st_area(agri.int.total)
#> Convert from m2 to km2
agri.int.total$AREA_AGRI_TOTAL <- agri.int.total$AREA_AGRI_TOTAL / 1000000
agri.int.total$AREA_AGRI_TOTAL <- round(agri.int.total$AREA_AGRI_TOTAL, digits = 3)
agri.int.total$AREA_AGRI_TOTAL <- as.numeric(agri.int.total$AREA_AGRI_TOTAL)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.total.shp"))
unlink(here("Out", "Tests", "agri.int.total.dbf"))
unlink(here("Out", "Tests", "agri.int.total.prj"))
unlink(here("Out", "Tests", "agri.int.total.shx"))
st_write(agri.int.total, here("Out", "Tests", "agri.int.total.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.total) <- NULL
agri.int.total <- agri.int.total |> 
  select(name, AREA_AGRI_TOTAL) |> 
  group_by(name) |> 
  summarise(AGRI_TOTAL = sum(AREA_AGRI_TOTAL))


#> 2. Intersect pcodes.clip with corine.int to calculate area of agri land ony within target county polygon
agri.int.clip <- st_intersection(pcodes.clip, corine.agri)
#> Calculate area of Corine agri land
agri.int.clip$AREA_AGRI_CLIP <- st_area(agri.int.clip)
#> Convert from m2 to km2
agri.int.clip$AREA_AGRI_CLIP <- agri.int.clip$AREA_AGRI_CLIP / 1000000
agri.int.clip$AREA_AGRI_CLIP <- round(agri.int.clip$AREA_AGRI_CLIP, digits = 3)
agri.int.clip$AREA_AGRI_CLIP <- as.numeric(agri.int.clip$AREA_AGRI_CLIP)
#> Export data for detailed visual checking in QGIS
#> Remove existing shapefile
unlink(here("Out", "Tests", "agri.int.clip.shp"))
unlink(here("Out", "Tests", "agri.int.clip.dbf"))
unlink(here("Out", "Tests", "agri.int.clip.prj"))
unlink(here("Out", "Tests", "agri.int.clip.shx"))
st_write(agri.int.clip, here("Out", "Tests", "agri.int.clip.shp"), quiet = TRUE)
#> Create grouped (by pcode) non-geo version of the table
st_geometry(agri.int.clip) <- NULL
agri.int.clip <- agri.int.clip |> 
  select(name, AREA_AGRI_CLIP) |> 
  group_by(name) |> 
  summarise(AGRI_CLIP = sum(AREA_AGRI_CLIP))


#> 3. Calculate percentage difference between the two sets of area calculations to gove % of agri land in each pcode district polygon
#> Merge the two data frames to show size of agri area within and outside target county
agri.merge <- merge(agri.int.total, agri.int.clip, by = "name", all.x = TRUE)
#> Round area calcs up to 1 decimal place (to negate effect of small amounts of agri land being lost when clipped)
agri.merge$AGRI_TOTAL <- round(agri.merge$AGRI_TOTAL, digits = 3)
agri.merge$AGRI_CLIP <- round(agri.merge$AGRI_CLIP, digits = 2)
#> Calculate percentage of agri land within target county 
agri.merge$PCENT_AGRI_LAND <- agri.merge$AGRI_CLIP/ agri.merge$AGRI_TOTAL
#> Round up
agri.merge$PCENT_AGRI_LAND <- round(agri.merge$PCENT_AGRI_LAND, digits = 3)



#> Extract postcode districts from the BPS source data ("db") which intersect with the active county polygon boundary
#> Do this via a merge between db and pcodes.int, keeping only matching records in a new data frame
#> Rename pcodes.in and drop geom
pcodes.active <- pcodes.int
st_geometry(pcodes.active) <- NULL
BPS.merge <- merge(db, pcodes.active, by.x = "PostcodePrefix_F202B", "name", all.x = FALSE)
#> Convert all NAs to zeros in data frame
BPS.merge[is.na(BPS.merge)] <- 0



#> BPS Calcs by year

#> 2020
#> Create table with baseline P1 (BPS + Greening) payments by postcode district for 2020 (no payments applied)
t1.2020 <- BPS.merge %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2020_Baseline = sum(`Basic payment scheme`) + sum(`Greening: practices beneficial for climate and environment`))
#> Check sum total of P1 for reference
sum.original.p1 <- sum(t1.2020$P1_2020_Baseline)
#> Merge with agri.merge data frame to append 2020 calcs and create new master table "t1"
t1 <- merge(t1.2020, agri.merge, by.x = "PostcodePrefix_F202B", by.y = "name")
#> #> Calculate P1 payment based on area of agri land within each postcode area
t1$P1_2020 <- t1$P1_2020_Baseline * t1$PCENT_AGRI_LAND
#> Round to 2 decimal places
t1$P1_2020 <- round(t1$P1_2020, digits = 2)



#> 2021
t1.2021 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2021$P1_2020 <- t1.2021$`Basic payment scheme` + t1.2021$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2021 payments
t1.2021 <- t1.2021 %>% 
  mutate(P1_2021 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.95,
                              (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.90,
                              (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.80,
                              P1_2020 > 150000 ~ P1_2020 * 0.75))
# Group by postcode an summarise
t1.2021 <- t1.2021 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2021 = sum(P1_2021))
#> Round
t1.2021$P1_2021 <- round(t1.2021$P1_2021, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2021, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2021 <- t1$P1_2021 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2021 <- round(t1$P1_2021, digits = 2)
#> Check sum
sum.p1.2021 <- sum(t1$P1_2021)



#> 2022
t1.2022 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2022$P1_2020 <- t1.2022$`Basic payment scheme` + t1.2022$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2022 payments
t1.2022 <- t1.2022 %>% 
   mutate(P1_2022 = case_when(P1_2020<=30000 ~ P1_2020* 0.80,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.75,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.65,
                             P1_2020> 150000 ~ P1_2020* 0.60))
# Group by postcode an summarise
t1.2022 <- t1.2022 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2022 = sum(P1_2022))
#> Round
t1.2022$P1_2022 <- round(t1.2022$P1_2022, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2022, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2022 <- t1$P1_2022 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2022 <- round(t1$P1_2022, digits = 2)
#> Check sum
sum.p1.2022 <- sum(t1$P1_2022)


#> 2023
t1.2023 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2023$P1_2020 <- t1.2023$`Basic payment scheme` + t1.2023$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2023 payments
t1.2023 <- t1.2023 %>% 
  mutate(P1_2023 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.65,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.60,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.50,
                             P1_2020 > 150000 ~ P1_2020 * 0.45))
# Group by postcode an summarise
t1.2023 <- t1.2023 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2023 = sum(P1_2023))
#> Round
t1.2023$P1_2023 <- round(t1.2023$P1_2023, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2023, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2023 <- t1$P1_2023 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2023 <- round(t1$P1_2023, digits = 2)
#> Check sum
sum.p1.2023 <- sum(t1$P1_2023)


#> 2024
t1.2024 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2024$P1_2020 <- t1.2024$`Basic payment scheme` + t1.2024$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2024 payments
t1.2024 <- t1.2024 %>% 
  mutate(P1_2024 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.50,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.45,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.35,
                             P1_2020 > 150000 ~ P1_2020 * 0.30))
# Group by postcode an summarise
t1.2024 <- t1.2024 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2024 = sum(P1_2024))
#> Round
t1.2024$P1_2024 <- round(t1.2024$P1_2024, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2024, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2024 <- t1$P1_2024 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2024 <- round(t1$P1_2024, digits = 2)
#> Check sum
sum.p1.2024 <- sum(t1$P1_2024)


#> 2025
t1.2025 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2025$P1_2020 <- t1.2025$`Basic payment scheme` + t1.2025$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2025 payments
t1.2025 <- t1.2025 %>% 
 mutate(P1_2025 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.40,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.35,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.25,
                             P1_2020 > 150000 ~ P1_2020 * 0.20))
# Group by postcode an summarise
t1.2025 <- t1.2025 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2025 = sum(P1_2025))
#> Round
t1.2025$P1_2025 <- round(t1.2025$P1_2025, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2025, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2025 <- t1$P1_2025 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2025 <- round(t1$P1_2025, digits = 2)
#> Check sum
sum.p1.2025 <- sum(t1$P1_2025)


#> 2026
t1.2026 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2026$P1_2020 <- t1.2026$`Basic payment scheme` + t1.2026$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2026 payments
t1.2026 <- t1.2026 %>% 
  mutate(P1_2026 = case_when(P1_2020 <=30000 ~ P1_2020 * 0.25,
                             (P1_2020 >30000 & P1_2020 <=50000) ~ P1_2020 * 0.25,
                             (P1_2020 >50000 & P1_2020 <=150000) ~ P1_2020 * 0.15,
                             P1_2020 > 150000 ~ P1_2020 * 0.15))
# Group by postcode an summarise
t1.2026 <- t1.2026 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2026 = sum(P1_2026))
#> Round
t1.2026$P1_2026 <- round(t1.2026$P1_2026, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2026, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2026 <- t1$P1_2026 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2026 <- round(t1$P1_2026, digits = 2)
#> Check sum
sum.p1.2026 <- sum(t1$P1_2026)


#> 2027
t1.2027 <- BPS.merge %>% 
  select(PostcodePrefix_F202B, `Basic payment scheme`, `Greening: practices beneficial for climate and environment`)
#> Column to hold total total P1 payments (i.e. BPS + Greening) - baseline for 2020
t1.2027$P1_2020 <- t1.2027$`Basic payment scheme` + t1.2027$`Greening: practices beneficial for climate and environment`
#> Add new column showing 2027 payments
t1.2027 <- t1.2027 %>% 
   mutate(P1_2027 = case_when(P1_2020<=30000 ~ P1_2020* 0.15,
                             (P1_2020>30000 & P1_2020<=50000) ~ P1_2020* 0.15,
                             (P1_2020>50000 & P1_2020<=150000) ~ P1_2020* 0.10,
                             P1_2020> 150000 ~ P1_2020* 0.10))
# Group by postcode an summarise
t1.2027 <- t1.2027 %>% 
  group_by(PostcodePrefix_F202B) %>% 
  summarise(P1_2027 = sum(P1_2027))
#> Round
t1.2027$P1_2027 <- round(t1.2027$P1_2027, digits = 2)
# merge with main P1 results table (m.)
t1 <- merge(t1, t1.2027, by.x = "PostcodePrefix_F202B", by.y = "PostcodePrefix_F202B", all.x = TRUE)
# Change values according to agi land area proportion
t1$P1_2027 <- t1$P1_2027 * t1$PCENT_AGRI_LAND #> Round
t1$P1_2027 <- round(t1$P1_2027, digits = 2)
#> Check sum
sum.p1.2027 <- sum(t1$P1_2027)

#> Convert all NAs to zeros in data frame
t1[is.na(t1)] <- 0



#> Create plot

#> P1 payments by year
p1.in <- as.data.frame(colSums(t1[6:13]))
#> Change rownames to column "Value"
p1.plot <- tibble::rownames_to_column(p1.in, "VALUE")
#> Extract year from string
p1.plot$VALUE <- sub("^.*([0-9]{4}).*", "\\1", p1.plot$VALUE)
names(p1.plot)[1]<-paste("Year")
names(p1.plot)[2]<-paste("Value_bps")

#> Print table t1 on web page
print(knitr::kable(t1, col.names = c("PC", "2020_Unadjusted", "Agri_Total", "Agri_In", "Agri_PC", "2020", "2021", "2022", "2023", "2024", "2025", "2026", "2027"), caption = paste0("Table 1.", i , " ", "P1 payments by National Park - ",  active_park)))

#> Add line breaks
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")


# Simple bar chart
plot1 <- ggplot(p1.plot, aes(x=Year, y=Value_bps)) + 
  theme_bw() +
  geom_bar(stat = "identity", fill="#2c66b8", width = 0.6) +
  geom_text(aes(label= paste0(round(Value_bps / 1000000, digits = 1), " M")), vjust = 1.5, colour = "white") +
  labs(title = paste0("Pillar 1 payments:", " ", active_park), x = "Year", y = "Value (£)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))
plot1

#> Add line breaks
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")
cat("\n")

#> Render on web page
print(plot1)

#> Export the plot
ggsave(here("Out", "P1", "Nat_Park", "Plot", paste0("P1_payments_", active_park, ".png")))

#> Export final t1 table
write_csv(t1, here("Out", "P1", "Nat_Park", "CSV", paste0("P1_payments_", active_park, ".csv")))

}
          
```

<br />
<br />


## 4. Agri-Environment 

### 4.1 ES - County-level

County-level analysis of Environmental Stewardship (ES) payments. Methods overview to follow. 


```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Get ES data
#> This dataset has been extracted from the latest 914/02/2022) CS data for England
#> The pole of inaccessibility for each ES polygon has been pre-computed in QGIS, and the points then clipped to the extent of the SW LEP to reduce processing overheads
ES <- st_read(here("In", "Shape", "AES", "ES_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

i <- 0
#> Initiate loop
for(active_county in counties){
  
#> Loop counter (for table caption number)
i <- i+1

#> Get a boundary shapefile for the active county
target_county <- counties.sw |>
  filter(NAME == active_county)


# #> Test county polygon (Cornwall) - need to automate for all counties - then districts
# test.county <- cornwall.sf

#> Intersect with target county polygon
int <- st_intersection(ES, target_county)

#> Create non-geom version 
ES.ng <- int
st_geometry(ES.ng) <- NULL

#> Filter records to get ones that were live in 2020
#> New start date field in date format
ES.ng$STARTDAT.2 <- as.Date(ES.ng$STARTDAT, format = "%d/%m/%Y") # correct lowercase y
#> New start date field in date format
ES.ng$ENDDATE.2 <- as.Date(ES.ng$ENDDATE, format = "%d/%m/%Y") # correct lowercase y

#> Create column for length of agreement in years
ES.ng$Years <- as.numeric(ES.ng$ENDDATE.2 - ES.ng$STARTDAT.2) / 365
ES.ng$Years <- round(ES.ng$Years, 0)
ES.ng$TOTCOST <- as.numeric(ES.ng$TOTCOST)

#> Create column for average cost
ES.ng$AV.YEAR.COST <- ES.ng$TOTCOST / ES.ng$Years
#> Change NAs to Zero
ES.ng$AV.YEAR.COST[is.na(ES.ng$AV.YEAR.COST)] <- 0

#> Export as CSV
write_csv(ES.ng, here("Out", "AES", "ES", "County", paste0("ES_Agreements_", active_county, ".csv")))


#> 2018 and 2019 baseline
#> Calculate the "baseline" for agreements live in 2018 - earliest end date is "2020-04-30" - so all records will be included
live.2018 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2040-12-31")   
#> Sum Av cost for annual total for 2018
x.2018 <- sum(live.2018$AV.YEAR.COST)
x.2019 <- sum(live.2018$AV.YEAR.COST)  #2019 is the same - as same number of live agreements running throughout 2019-2018
#> Create new dataframe to hold this
totals <- c(x.2018, x.2019)
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0)))
#> Add figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)



#> Work out 2020 totals
#> Filter for agreements ending in 2020
end.2020 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2020-12-31")
#> Work out how many days in year that agreement running for
end.2020$YearStart <- as.Date("2020-01-01")
end.2020$Days <- as.numeric(end.2020$ENDDATE.2 - end.2020$YearStart)
#> Work out proportion of year agreement is active
end.2020$Year_Prop <- end.2020$Days / 365
#> New column for cost of 2020 based on proportion
end.2020$Cost_Actual <- end.2020$Year_Prop * end.2020$AV.YEAR.COST
#> Total amount for agreements ending in 2020
tot.2020 <- sum(end.2020$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2020 <- x.2018 - tot.2020
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)



#> Work out 2021 totals
#> Filter for agreements ending in 2021
end.2021 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2021-01-01", ENDDATE.2 <= "2021-12-31")
#> Work out how many days in year that agreement running for
end.2021$YearStart <- as.Date("2021-01-01")
end.2021$Days <- as.numeric(end.2021$ENDDATE.2 - end.2021$YearStart)
#> Work out proportion of year agreement is active
end.2021$Year_Prop <- end.2021$Days / 365
#> New column for cost of 2021 based on proportion
end.2021$Cost_Actual <- end.2021$Year_Prop * end.2021$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2021 <- sum(end.2021$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2021 <- x.2018 - (tot.2020 + tot.2021)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021)
#> Insert figure for 2021
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)



#> Work out 2022 totals
#> Filter for agreements ending in 2022
end.2022 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2022-01-01", ENDDATE.2 <= "2022-12-31")
#> Work out how mnay days in year that agreement running for
end.2022$YearStart <- as.Date("2022-01-01")
end.2022$Days <- as.numeric(end.2022$ENDDATE.2 - end.2022$YearStart)
#> Work out proipertion of year agreement is active
end.2022$Year_Prop <- end.2022$Days / 365
#> New column for cost of 2021 based on proportion
end.2022$Cost_Actual <- end.2022$Year_Prop * end.2022$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2022 <- sum(end.2022$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2022  <- x.2018 - (tot.2021 + tot.2020 + tot.2022)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)


#> Work out 2023 totals
#> Filter for agreements ending in 2023
end.2023 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2023-01-01", ENDDATE.2 <= "2023-12-31")
#> Work out how mnay days in year that agreement running for
end.2023$YearStart <- as.Date("2023-01-01")
end.2023$Days <- as.numeric(end.2023$ENDDATE.2 - end.2023$YearStart)
#> Work out proipertion of year agreement is active
end.2023$Year_Prop <- end.2023$Days / 365
#> New column for cost of 2021 based on proportion
end.2023$Cost_Actual <- end.2023$Year_Prop * end.2023$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2023 <- sum(end.2023$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2023  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)


#> Work out 2024 totals
#> Filter for agreements ending in 2024
end.2024 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2024-01-01", ENDDATE.2 <= "2024-12-31")
#> Work out how mnay days in year that agreement running for
end.2024$YearStart <- as.Date("2024-01-01")
end.2024$Days <- as.numeric(end.2024$ENDDATE.2 - end.2024$YearStart)
#> Work out proipertion of year agreement is active
end.2024$Year_Prop <- end.2024$Days / 365
#> New column for cost of 2021 based on proportion
end.2024$Cost_Actual <- end.2024$Year_Prop * end.2024$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2024 <- sum(end.2024$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2024  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023 + tot.2024)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023, x.2024)
#> Insert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)


# Export ES payments summary table
write_csv(df, here("Out", "AES", "ES", "County", "CSV", paste0("ES_payments_Summary_", active_county, ".csv")))

#> Print table district.summary on web page
print(knitr::kable(df, caption = paste0("Table 4.1.", i , " ", "ES payments - ",  active_county)))


#> Plot data as bar chart
#> Make long
df.plot <- melt(df)
#> Extract year from string
names(df.plot)[1]<-paste("Year")
names(df.plot)[2]<-paste("Value_es")
df.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df.plot$Year)

# Simple bar chart
plot.es <- ggplot(df.plot, aes(x=Year, y=Value_es)) + 
  geom_bar(stat = "identity", fill="#b3a96fff", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Environmental Stewardship payments: ", active_county), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_es / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.es
print(plot.es)
#> Export the plot
ggsave(here("Out", "AES", "ES", "County", "Plot", paste0("ES_payments_", active_county, ".png")), width = 7, height = 5)


#> Render table on web page



}



```



### 4.2 ES - District-level


District-level analysis of Environmental Stewardship (ES) payments. Methods overview to follow. 

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Get ES data
#> This dataset has been extracted from the latest 914/02/2022) CS data for England
#> The pole of inaccessibility for each ES polygon has been pre-computed in QGIS, and the points then clipped to the extent of the SW LEP to reduce processing overheads
ES <- st_read(here("In", "Shape", "AES", "ES_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

#> Get district boundary data for SW counties
districts.sw <- st_read(here("In", "Shape", "Districts.SW.UPDATED.2.shp"), quiet = TRUE)

#? Remove string "(B)" from district names
# # districts.sw$NAME <- str_remove_all(districts.sw$NAME, "(B)")
districts.sw$NAME<- gsub("\\s*\\([^\\)]+\\)", "", districts.sw$NAME)
#> Trim WS
districts.sw$NAME<- trimws(districts.sw$NAME)
# glimpse(districts.sw)
  
#> Create list for loop
districts.list <- as.list(districts.sw$NAME)

i <- 0
#> Initiate loop
for(active_district in districts.list){

#> Loop counter (for table caption number)
i <- i+1

#> Get a boundary shapefile for the active county
target_district <- districts.sw |>
  filter(NAME == active_district)


# #> Test county polygon (Cornwall) - need to automate for all counties - then districts
# test.county <- cornwall.sf

#> Intersect with target county polygon
int <- st_intersection(ES, target_district)

#> Create non-geom version 
ES.ng <- int
st_geometry(ES.ng) <- NULL

#> Filter records to get ones that were live in 2020
#> New start date field in date format
ES.ng$STARTDAT.2 <- as.Date(ES.ng$STARTDAT, format = "%d/%m/%Y") # correct lowercase y
#> New start date field in date format
ES.ng$ENDDATE.2 <- as.Date(ES.ng$ENDDATE, format = "%d/%m/%Y") # correct lowercase y

#> Create column for length of agreement in years
ES.ng$Years <- as.numeric(ES.ng$ENDDATE.2 - ES.ng$STARTDAT.2) / 365
ES.ng$Years <- round(ES.ng$Years, 0)
ES.ng$TOTCOST <- as.numeric(ES.ng$TOTCOST)

#> Create column for average cost
ES.ng$AV.YEAR.COST <- ES.ng$TOTCOST / ES.ng$Years
#> Change NAs to Zero
ES.ng$AV.YEAR.COST[is.na(ES.ng$AV.YEAR.COST)] <- 0

#> Export as CSV
write_csv(ES.ng, here("Out", "AES", "ES", "District", "CSV", paste0("ES_Agreements_", active_district, ".csv")))


#> 2018 and 2019 baseline
#> Calculate the "baseline" for agreements live in 2018 - earliest end date is "2020-04-30" - so all records will be included
live.2018 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2040-12-31")   
#> Sum Av cost for annual total for 2018
x.2018 <- sum(live.2018$AV.YEAR.COST)
x.2019 <- sum(live.2018$AV.YEAR.COST)  #2019 is the same - as same number of live agreements running throughout 2019-2018
#> Create new dataframe to hold this
totals <- c(x.2018, x.2019)
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0)))
#> Add figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)



#> Work out 2020 totals
#> Filter for agreements ending in 2020
end.2020 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2020-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2020)[1] != 0) {
#> Work out how many days in year that agreement running for
end.2020$YearStart <- as.Date("2020-01-01")
end.2020$Days <- as.numeric(end.2020$ENDDATE.2 - end.2020$YearStart)
#> Work out proportion of year agreement is active
end.2020$Year_Prop <- end.2020$Days / 365
#> New column for cost of 2020 based on proportion
end.2020$Cost_Actual <- end.2020$Year_Prop * end.2020$AV.YEAR.COST
#> Total amount for agreements ending in 2020
tot.2020 <- sum(end.2020$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2020 <- x.2018 - tot.2020
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
  
tot.2020 = 0
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2020 <- x.2018 - tot.2020
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}





#> Work out 2021 totals
#> Filter for agreements ending in 2021
end.2021 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2021-01-01", ENDDATE.2 <= "2021-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2021)[1] != 0) {
#> Work out how many days in year that agreement running for
end.2021$YearStart <- as.Date("2021-01-01")
end.2021$Days <- as.numeric(end.2021$ENDDATE.2 - end.2021$YearStart)
#> Work out proportion of year agreement is active
end.2021$Year_Prop <- end.2021$Days / 365
#> New column for cost of 2021 based on proportion
end.2021$Cost_Actual <- end.2021$Year_Prop * end.2021$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2021 <- sum(end.2021$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2021 <- x.2018 - (tot.2020 + tot.2021)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021)
#> Insert figure for 2021
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
  
end.2021 = 0
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2021 <- x.2018 - (tot.2020 + tot.2021)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021)
#> Insert figure for 2021
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}


#> Work out 2022 totals
#> Filter for agreements ending in 2022
end.2022 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2022-01-01", ENDDATE.2 <= "2022-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2022)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2022$YearStart <- as.Date("2022-01-01")
end.2022$Days <- as.numeric(end.2022$ENDDATE.2 - end.2022$YearStart)
#> Work out proipertion of year agreement is active
end.2022$Year_Prop <- end.2022$Days / 365
#> New column for cost of 2021 based on proportion
end.2022$Cost_Actual <- end.2022$Year_Prop * end.2022$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2022 <- sum(end.2022$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2022  <- x.2018 - (tot.2021 + tot.2020 + tot.2022)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
end.2022 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2022  <- x.2018 - (tot.2021 + tot.2020 + tot.2022)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}



#> Work out 2023 totals
#> Filter for agreements ending in 2023
end.2023 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2023-01-01", ENDDATE.2 <= "2023-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2023)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2023$YearStart <- as.Date("2023-01-01")
end.2023$Days <- as.numeric(end.2023$ENDDATE.2 - end.2023$YearStart)
#> Work out proipertion of year agreement is active
end.2023$Year_Prop <- end.2023$Days / 365
#> New column for cost of 2021 based on proportion
end.2023$Cost_Actual <- end.2023$Year_Prop * end.2023$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2023 <- sum(end.2023$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2023  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
} else {
  
end.2023 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2023  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
}


#> Work out 2024 totals
#> Filter for agreements ending in 2024
end.2024 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2024-01-01", ENDDATE.2 <= "2024-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2024)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2024$YearStart <- as.Date("2024-01-01")
end.2024$Days <- as.numeric(end.2024$ENDDATE.2 - end.2024$YearStart)
#> Work out proipertion of year agreement is active
end.2024$Year_Prop <- end.2024$Days / 365
#> New column for cost of 2021 based on proportion
end.2024$Cost_Actual <- end.2024$Year_Prop * end.2024$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2024 <- sum(end.2024$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2024  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023 + tot.2024)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023, x.2024)
#> Insert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
} else {
  
end.2024 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2024  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023 + tot.2024)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023, x.2024)

}


#> If there are any negative values in df, convert these to zero
df[df <0] <- 0



# Export ES payments summary table
write_csv(df, here("Out", "AES", "ES", "District", "CSV", paste0("ES_payments_Summary_", active_district, ".csv")))

#> Print table district.summary on web page
print(knitr::kable(df, caption = paste0("Table 4.2.", i , " ", "ES payments - ",  active_district)))


#> Plot data as bar chart
#> Make long
df.plot <- melt(df)
#> Extract year from string
names(df.plot)[1]<-paste("Year")
names(df.plot)[2]<-paste("Value_es")
df.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df.plot$Year)

# Simple bar chart
plot.es <- ggplot(df.plot, aes(x=Year, y=Value_es)) + 
  geom_bar(stat = "identity", fill="#b3a96fff", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Environmental Stewardship payments: ", active_district), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_es / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.es
print(plot.es)
#> Export the plot
ggsave(here("Out", "AES", "ES", "District", "Plot", paste0("ES_payments_", active_district, ".png")), width = 7, height = 5)




}



```


### 4.3 ES - National Parks


National Park-level analysis of Environmental Stewardship (ES) payments. Methods overview to follow. 

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Get ES data
#> This dataset has been extracted from the latest 914/02/2022) CS data for England
#> The pole of inaccessibility for each ES polygon has been pre-computed in QGIS, and the points then clipped to the extent of the SW LEP to reduce processing overheads
ES <- st_read(here("In", "Shape", "AES", "ES_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

#> Create filter string (get names first!)
nat.parks.list <- c("Exmoor", "Dartmoor")

#> Sequential integer counter (for figure numbers)
i <-0 

#> Initiate loop
for(active_park in nat.parks.list){
  
#> Loop counter (for table caption number)
i <- i+1

#> Select target county (this will be start of loop)
target_park <- nat.parks|> 
  filter(NAME == active_park)

# #> Test county polygon (Cornwall) - need to automate for all counties - then districts
# test.county <- cornwall.sf

#> Intersect with target county polygon
int <- st_intersection(ES, target_park)

#> Create non-geom version 
ES.ng <- int
st_geometry(ES.ng) <- NULL

#> Filter records to get ones that were live in 2020
#> New start date field in date format
ES.ng$STARTDAT.2 <- as.Date(ES.ng$STARTDAT, format = "%d/%m/%Y") # correct lowercase y
#> New start date field in date format
ES.ng$ENDDATE.2 <- as.Date(ES.ng$ENDDATE, format = "%d/%m/%Y") # correct lowercase y

#> Create column for length of agreement in years
ES.ng$Years <- as.numeric(ES.ng$ENDDATE.2 - ES.ng$STARTDAT.2) / 365
ES.ng$Years <- round(ES.ng$Years, 0)
ES.ng$TOTCOST <- as.numeric(ES.ng$TOTCOST)

#> Create column for average cost
ES.ng$AV.YEAR.COST <- ES.ng$TOTCOST / ES.ng$Years
#> Change NAs to Zero
ES.ng$AV.YEAR.COST[is.na(ES.ng$AV.YEAR.COST)] <- 0

#> Export as CSV
write_csv(ES.ng, here("Out", "AES", "ES", "Nat_Park", "CSV", paste0("ES_Agreements_", active_park, ".csv")))


#> 2018 and 2019 baseline
#> Calculate the "baseline" for agreements live in 2018 - earliest end date is "2020-04-30" - so all records will be included
live.2018 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2040-12-31")   
#> Sum Av cost for annual total for 2018
x.2018 <- sum(live.2018$AV.YEAR.COST)
x.2019 <- sum(live.2018$AV.YEAR.COST)  #2019 is the same - as same number of live agreements running throughout 2019-2018
#> Create new dataframe to hold this
totals <- c(x.2018, x.2019)
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0)))
#> Add figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)



#> Work out 2020 totals
#> Filter for agreements ending in 2020
end.2020 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(STARTDAT.2 <= "2017-12-31", ENDDATE.2 <= "2020-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2020)[1] != 0) {
#> Work out how many days in year that agreement running for
end.2020$YearStart <- as.Date("2020-01-01")
end.2020$Days <- as.numeric(end.2020$ENDDATE.2 - end.2020$YearStart)
#> Work out proportion of year agreement is active
end.2020$Year_Prop <- end.2020$Days / 365
#> New column for cost of 2020 based on proportion
end.2020$Cost_Actual <- end.2020$Year_Prop * end.2020$AV.YEAR.COST
#> Total amount for agreements ending in 2020
tot.2020 <- sum(end.2020$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2020 <- x.2018 - tot.2020
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
  
tot.2020 = 0
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2020 <- x.2018 - tot.2020
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}





#> Work out 2021 totals
#> Filter for agreements ending in 2021
end.2021 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2021-01-01", ENDDATE.2 <= "2021-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2021)[1] != 0) {
#> Work out how many days in year that agreement running for
end.2021$YearStart <- as.Date("2021-01-01")
end.2021$Days <- as.numeric(end.2021$ENDDATE.2 - end.2021$YearStart)
#> Work out proportion of year agreement is active
end.2021$Year_Prop <- end.2021$Days / 365
#> New column for cost of 2021 based on proportion
end.2021$Cost_Actual <- end.2021$Year_Prop * end.2021$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2021 <- sum(end.2021$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2021 <- x.2018 - (tot.2020 + tot.2021)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021)
#> Insert figure for 2021
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
  
end.2021 = 0
#> Subtract from 2018 baseline total to calculate final total for 2020
x.2021 <- x.2018 - (tot.2020 + tot.2021)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021)
#> Insert figure for 2021
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}


#> Work out 2022 totals
#> Filter for agreements ending in 2022
end.2022 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2022-01-01", ENDDATE.2 <= "2022-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2022)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2022$YearStart <- as.Date("2022-01-01")
end.2022$Days <- as.numeric(end.2022$ENDDATE.2 - end.2022$YearStart)
#> Work out proipertion of year agreement is active
end.2022$Year_Prop <- end.2022$Days / 365
#> New column for cost of 2021 based on proportion
end.2022$Cost_Actual <- end.2022$Year_Prop * end.2022$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2022 <- sum(end.2022$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2022  <- x.2018 - (tot.2021 + tot.2020 + tot.2022)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

} else {
end.2022 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2022  <- x.2018 - (tot.2021 + tot.2020 + tot.2022)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)

}



#> Work out 2023 totals
#> Filter for agreements ending in 2023
end.2023 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2023-01-01", ENDDATE.2 <= "2023-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2023)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2023$YearStart <- as.Date("2023-01-01")
end.2023$Days <- as.numeric(end.2023$ENDDATE.2 - end.2023$YearStart)
#> Work out proipertion of year agreement is active
end.2023$Year_Prop <- end.2023$Days / 365
#> New column for cost of 2021 based on proportion
end.2023$Cost_Actual <- end.2023$Year_Prop * end.2023$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2023 <- sum(end.2023$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2023  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
} else {
  
end.2023 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2023  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023)
#> AInsert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
}


#> Work out 2024 totals
#> Filter for agreements ending in 2024
end.2024 <- ES.ng %>%
  select(AGREF, TOTCOST, Years, AV.YEAR.COST, STARTDAT.2, ENDDATE.2, Years) %>% 
  filter(ENDDATE.2  >= "2024-01-01", ENDDATE.2 <= "2024-12-31")
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(end.2024)[1] != 0) {
#> Work out how mnay days in year that agreement running for
end.2024$YearStart <- as.Date("2024-01-01")
end.2024$Days <- as.numeric(end.2024$ENDDATE.2 - end.2024$YearStart)
#> Work out proipertion of year agreement is active
end.2024$Year_Prop <- end.2024$Days / 365
#> New column for cost of 2021 based on proportion
end.2024$Cost_Actual <- end.2024$Year_Prop * end.2024$AV.YEAR.COST
#> Total amount for agreements ending in 2021
tot.2024 <- sum(end.2024$Cost_Actual)
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2024  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023 + tot.2024)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023, x.2024)
#> Insert figure for 2018
df <- miscTools::insertRow(ES_Summary, 1, totals)
df <- as.data.frame(df)
} else {
  
end.2024 = 0
#> Subtract from 2018 baseline total to calculate final total for 2021
x.2024  <- x.2018 - (tot.2021 + tot.2020 + tot.2022 + tot.2023 + tot.2024)
#> Update df
ES_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals <- c(x.2018, x.2019, x.2020, x.2021, x.2022, x.2023, x.2024)

}


# Export ES payments summary table
write_csv(df, here("Out", "AES", "ES", "Nat_Park", "CSV", paste0("ES_payments_Summary_", active_park, ".csv")))

#> Print table district.summary on web page
print(knitr::kable(df, caption = paste0("Table 4.3.", i , " ", "ES payments - ",  active_park)))


#> Plot data as bar chart
#> Make long
df.plot <- melt(df)
#> Extract year from string
names(df.plot)[1]<-paste("Year")
names(df.plot)[2]<-paste("Value_es")
df.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df.plot$Year)

# Simple bar chart
plot.es <- ggplot(df.plot, aes(x=Year, y=Value_es)) + 
  geom_bar(stat = "identity", fill="#b3a96fff", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Environmental Stewardship payments: ", active_park), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_es / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.es
print(plot.es)
#> Export the plot
ggsave(here("Out", "AES", "ES", "Nat_Park", "Plot", paste0("ES_payments_", active_park, ".png")), width = 7, height = 5)




}


```




### 4.4 CS - County-level


County-level analysis of Countryside Stewardship (CS) payments. Methods overview to follow. 

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}


#> Get data
CS <- st_read(here("In", "Shape", "AES", "CS_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

#> Initiate counter (for figure numbers)
i <- 0
#> Initiate loop
for(active_county in counties){
#> Loop counter (for table caption number)
i <- i+1
#> Get a boundary shapefile for the active county
target_county <- counties.sw |>
filter(NAME == active_county)

# #> TESTING - one county at a time
# target_county <- counties.gb |>
#   filter(NAME == "Dorset")


#> Intersect with target county polygon
int <- st_intersection(CS, target_county)

#> Rename intersected data
CS.ng <- int

#> New start date field in date format
CS.ng$STARTDATE.2 <- lubridate::dmy_hms(CS.ng$STARTDATE) 
#> New end date field in date format
CS.ng$ENDDATE.2 <- lubridate::dmy_hms(CS.ng$ENDDATE) 
#> Format dates
CS.ng$STARTDATE.2 <- as.Date(CS.ng$STARTDATE.2, format = "%d/%m/%Y")
CS.ng$ENDDATE.2 <- as.Date(CS.ng$ENDDATE.2, format = "%d/%m/%Y")

#> Create a column to get number of years
CS.ng$Years <- as.numeric(CS.ng$ENDDATE.2 - CS.ng$STARTDATE.2)
CS.ng$Years <- CS.ng$Years /365
CS.ng$Years <- round(CS.ng$Years, 0)
#> List of agreement duration in years - unique durations
years.unique <- unique(CS.ng$Years)

# #> Export table for team use
# write_csv(CS.ng, here("Out", "AES", "CS", "County", "CSV", paste0("CS_Agreements_", active_county, ".csv")))


#> Export table for team use
write_csv(CS.ng, here("Out", "AES", "CS", "County", "CSV", paste0("CS_Agreements_", active_county, "Test.csv")))


#Create individual year columns to assign agreements to different years based on start date and duration - code for that to follow below
CS.ng$y.2016 <- 0
CS.ng$y.2017 <- 0 
CS.ng$y.2018 <- 0
CS.ng$y.2019 <- 0
CS.ng$y.2020 <- 0
CS.ng$y.2021 <- 0
CS.ng$y.2022 <- 0
CS.ng$y.2023 <- 0
CS.ng$y.2024 <- 0

#> Get unique combinations of agreements-years
unique.agree2 <- count(CS.ng, STARTDATE.2, Years) %>% 
  ungroup()
#> Export
write_csv(unique.agree2, (here("Out", "AES", "CS", "CS_Unique_Agree-Year_for_checking.csv")))


#> 1. Agreements starting in 2016 running for 10 years
cs.2016.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2016-01-01") & STARTDATE.2 <= as.Date("2016-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2016.10)[1] != 0) {
#> Update relevant cols
cs.2016.10$y.2016 = 1
cs.2016.10$y.2017 = 1
cs.2016.10$y.2018 = 1
cs.2016.10$y.2019 = 1
cs.2016.10$y.2020 = 1
cs.2016.10$y.2021 = 1
cs.2016.10$y.2022 = 1
cs.2016.10$y.2023 = 1
cs.2016.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2016[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2016
CS.ng$y.2017[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2017
CS.ng$y.2018[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2018
CS.ng$y.2019[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2019
CS.ng$y.2020[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2020
CS.ng$y.2021[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2021
CS.ng$y.2022[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2022
CS.ng$y.2023[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2023
CS.ng$y.2024[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2024
}


#> 2. Agreements starting in 2017 running for 10 years
cs.2017.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2017-01-01") & STARTDATE.2 <= as.Date("2017-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2017.10)[1] != 0) {
#> Update relevant cols
cs.2017.10$y.2017 = 1
cs.2017.10$y.2018 = 1
cs.2017.10$y.2019 = 1
cs.2017.10$y.2020 = 1
cs.2017.10$y.2021 = 1
cs.2017.10$y.2022 = 1
cs.2017.10$y.2023 = 1
cs.2017.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2017[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2017
CS.ng$y.2018[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2018
CS.ng$y.2019[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2019
CS.ng$y.2020[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2020
CS.ng$y.2021[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2021
CS.ng$y.2022[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2022
CS.ng$y.2023[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2023
CS.ng$y.2024[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2024
}



#> 3. Agreements starting in 2018 running for 5 years 
cs.2018.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.5)[1] != 0) {
#> Update relevant cols
cs.2018.5$y.2018 = 1
cs.2018.5$y.2019 = 1
cs.2018.5$y.2020 = 1
cs.2018.5$y.2021 = 1
cs.2018.5$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2018
CS.ng$y.2019[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2019
CS.ng$y.2020[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2020
CS.ng$y.2021[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2021
CS.ng$y.2022[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2022
}



#> 4. Agreements starting in 2018 running for 10 years 
cs.2018.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.10)[1] != 0) {
#> Update relevant cols
cs.2018.10$y.2018 = 1
cs.2018.10$y.2019 = 1
cs.2018.10$y.2020 = 1
cs.2018.10$y.2021 = 1
cs.2018.10$y.2022 = 1
cs.2018.10$y.2023 = 1
cs.2018.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2018
CS.ng$y.2019[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2019
CS.ng$y.2020[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2020
CS.ng$y.2021[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2021
CS.ng$y.2022[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2022
CS.ng$y.2023[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2023
CS.ng$y.2024[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2024
}



#> 5. Agreements starting in 2019 running for 5 years 
cs.2019.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.5)[1] != 0) {
#> Update relevant cols
cs.2019.5$y.2019 = 1
cs.2019.5$y.2020 = 1
cs.2019.5$y.2021 = 1
cs.2019.5$y.2022 = 1
cs.2019.5$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2019
CS.ng$y.2020[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2020
CS.ng$y.2021[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2021
CS.ng$y.2022[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2022
CS.ng$y.2023[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2023
}



#> 6. Agreements starting in 2019 running for 10 years 
cs.2019.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.10)[1] != 0) {
#> Update relevant cols
cs.2019.10$y.2019 = 1
cs.2019.10$y.2020 = 1
cs.2019.10$y.2021 = 1
cs.2019.10$y.2022 = 1
cs.2019.10$y.2023 = 1
cs.2019.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2019
CS.ng$y.2020[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2020
CS.ng$y.2021[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2021
CS.ng$y.2022[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2022
CS.ng$y.2023[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2023
CS.ng$y.2024[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2024
}



#> 7. Agreements starting in 20 running for 2years 
cs.2020.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.2)[1] != 0) {
#> Update relevant cols
cs.2020.2$y.2020 = 1
cs.2020.2$y.2021 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2020
CS.ng$y.2021[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2021
}



#> 8. Agreements starting in 20 running for 5 years 
cs.2020.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.5)[1] != 0) {
#> Update relevant cols
cs.2020.5$y.2020 = 1
cs.2020.5$y.2021 = 1
cs.2020.5$y.2022 = 1
cs.2020.5$y.2023 = 1
cs.2020.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2020
CS.ng$y.2021[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2021
CS.ng$y.2022[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2022
CS.ng$y.2023[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2023
CS.ng$y.2024[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2024
}



#> 9. Agreements starting in 20 running for 10 years 
cs.2020.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.10)[1] != 0) {
#> Update relevant cols
cs.2020.10$y.2020 = 1
cs.2020.10$y.2021 = 1
cs.2020.10$y.2022 = 1
cs.2020.10$y.2023 = 1
cs.2020.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2020
CS.ng$y.2021[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2021
CS.ng$y.2022[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2022
CS.ng$y.2023[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2023
CS.ng$y.2024[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2024
}



#> 10. Agreements starting in 21 running for 2 years 
cs.2021.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.2)[1] != 0) {
#> Update relevant cols
cs.2021.2$y.2021 = 1
cs.2021.2$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2021
CS.ng$y.2022[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2022
}


#> 11. Agreements starting in 21 running for 5 years 
cs.2021.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.5 )[1] != 0) {
#> Update relevant cols
cs.2021.5$y.2021 = 1
cs.2021.5$y.2022 = 1
cs.2021.5$y.2023 = 1
cs.2021.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2021
CS.ng$y.2022[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2022
CS.ng$y.2023[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2023
CS.ng$y.2024[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2024
}



#> 11. Agreements starting in 21 running for 10 years 
cs.2021.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.10)[1] != 0) {
#> Update relevant cols
cs.2021.10$y.2021 = 1
cs.2021.10$y.2022 = 1
cs.2021.10$y.2023 = 1
cs.2021.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2021
CS.ng$y.2022[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2022
CS.ng$y.2023[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2023
CS.ng$y.2024[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2024
}



#> 12. Agreements starting in 21 running for 20 years 
cs.2021.20 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 20)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.20 )[1] != 0) {
#> Update relevant cols
cs.2021.20$y.2021 = 1
cs.2021.20$y.2022 = 1
cs.2021.20$y.2023 = 1
cs.2021.20$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2021
CS.ng$y.2022[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2022
CS.ng$y.2023[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2023
CS.ng$y.2024[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2024
}



#> 13. Agreements starting in 22 running for 2 years 
cs.2022.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.2)[1] != 0) {
#> Update relevant cols
cs.2022.2$y.2022 = 1
cs.2022.2$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2022
CS.ng$y.2023[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2023
}



#> 14. Agreements starting in 22 running for 5 years 
cs.2022.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.5)[1] != 0) {
#> Update relevant cols
cs.2022.5$y.2022 = 1
cs.2022.5$y.2023 = 1
cs.2022.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2022
CS.ng$y.2023[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2023
CS.ng$y.2024[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2024
}



#> 15. Agreements starting in 22 running for 10 years 
cs.2022.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.10)[1] != 0) {
#> Update relevant cols
cs.2022.10$y.2022 = 1
cs.2022.10$y.2023 = 1
cs.2022.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2022
CS.ng$y.2023[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2023
CS.ng$y.2024[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2024
}



# Remove records where average annual cost id "unavailable"
CS.final <- CS.ng[!(CS.ng$AVGANNCOST=="*Unavailable"),]



# Export final raw data table
write_csv(CS.final, here("Out", "AES", "CS", "County", "CSV", paste0("CS_", active_county, "_Raw_Processed.csv")))

# # Export final raw data table - TESTING
# write_csv(CS.final, here("Out", "AES", "CS", "County", "CSV", paste0("CS__Raw_Processed_Test.csv")))



# Change annual cost column to numerical
CS.final$AVGANNCOST <- as.numeric(CS.final$AVGANNCOST)
CS.final$AVGANNCOST <- round(CS.final$AVGANNCOST, 2)


#> Calculate annual costs
#> Total for 2018
CS.2018.Total <- CS.final %>% 
  filter(y.2018 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2018 <- sum(CS.2018.Total$AVGANNCOST)

#> Total for 2019
CS.2019.Total <- CS.final %>% 
  filter(y.2019 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2019 <- sum(CS.2019.Total$AVGANNCOST)


#> Total for 2020
CS.2020.Total <- CS.final %>% 
  filter(y.2020 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2020 <- sum(CS.2020.Total$AVGANNCOST)


#> Total for 2021
CS.2021.Total <- CS.final %>% 
  filter(y.2021 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2021 <- sum(CS.2021.Total$AVGANNCOST)

#> Total for 2022
CS.2022.Total <- CS.final %>% 
  filter(y.2022 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2022 <- sum(CS.2022.Total$AVGANNCOST)

#> Total for 2023
CS.2023.Total <- CS.final %>% 
  filter(y.2023 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2023 <- sum(CS.2023.Total$AVGANNCOST)

#> Total for 2024
CS.2024.Total <- CS.final %>% 
  filter(y.2024 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2024 <- sum(CS.2024.Total$AVGANNCOST)


#> Create data frame of annual costs
CS_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals.cs <- c(CS.sum.2018, CS.sum.2019, CS.sum.2020, CS.sum.2021, CS.sum.2022, CS.sum.2023, CS.sum.2024)
#> Insert figure for 2018
df2 <- miscTools::insertRow(CS_Summary, 1, totals.cs)
df2 <- as.data.frame(df2)

#> Print table district.summary on web page
print(knitr::kable(df2, caption = paste0("Table 4.4.", i , " ", "CS payments - ",  active_county)))

#> Make long
df2.plot <- melt(df2)
#> Extract year from string
names(df2.plot)[1]<-paste("Year")
names(df2.plot)[2]<-paste("Value_cs")
df2.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df2.plot$Year)

# Simple bar chart
plot.cs <- ggplot(df2.plot, aes(x=Year, y=Value_cs)) + 
  geom_bar(stat = "identity", fill="#e38d0b", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Countryside Stewardship payments: ", active_county), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_cs / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white", size = 3.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.cs
print(plot.cs)


#> Export the plot
ggsave(here("Out", "AES", "CS", "County", "Plot", paste0("CS_payments_", active_county, ".png")), width = 7, height = 5)

# #> Export the plot - TESTING
# ggsave(here("Out", "AES", "CS", "County", "Plot", paste0("CS_payments_County_Test.png")), width = 7, height = 5)


#Export table
write_csv(df2, here("Out", "AES", "CS", "County", "CSV", paste0("CS_payments_", active_county, ".csv")))


# #Export table - TESTING
# write_csv(df2, here("Out", "AES", "CS", "County", "CSV", "CS_payments_County_Test.csv"))

}



```




### 4.5 CS - District-level

District-level analysis of Countryside Stewardship (CS) payments. Methods overview to follow. 

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}


#> Get data
CS <- st_read(here("In", "Shape", "AES", "CS_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

#> Get district boundary data for SW counties
districts.sw <- st_read(here("In", "Shape", "Districts.SW.UPDATED.2.shp"), quiet = TRUE)

#? Remove string "(B)" from district names
# # districts.sw$NAME <- str_remove_all(districts.sw$NAME, "(B)")
districts.sw$NAME<- gsub("\\s*\\([^\\)]+\\)", "", districts.sw$NAME)
#> Trim WS
districts.sw$NAME<- trimws(districts.sw$NAME)
# glimpse(districts.sw)
  
#> Create list for loop
districts.list <- as.list(districts.sw$NAME)



i <- 0
#> Initiate loop
for(active_district in districts.list){

#> Loop counter (for table caption number)
i <- i+1

#> Get a boundary shapefile for the active county
target_district <- districts.sw |>
  filter(NAME == active_district)


#> Intersect with target county polygon
int <- st_intersection(CS, target_district)

#> Rename intersected data
CS.ng <- int

#> New start date field in date format
CS.ng$STARTDATE.2 <- lubridate::dmy_hms(CS.ng$STARTDATE) 
#> New end date field in date format
CS.ng$ENDDATE.2 <- lubridate::dmy_hms(CS.ng$ENDDATE) 
#> Format dates
CS.ng$STARTDATE.2 <- as.Date(CS.ng$STARTDATE.2, format = "%d/%m/%Y")
CS.ng$ENDDATE.2 <- as.Date(CS.ng$ENDDATE.2, format = "%d/%m/%Y")

#> Create a column to get number of years
CS.ng$Years <- as.numeric(CS.ng$ENDDATE.2 - CS.ng$STARTDATE.2)
CS.ng$Years <- CS.ng$Years /365
CS.ng$Years <- round(CS.ng$Years, 0)
#> List of agreement duration in years - unique duration
years.unique <- unique(CS.ng$Years)

# #> Export table for team use
# write_csv(CS.ng, here("Out", "AES", "CS", "County", "CSV", paste0("CS_Agreements_", active_county, ".csv")))


#> Export table for team use
write_csv(CS.ng, here("Out", "AES", "CS", "District", "CSV", paste0("CS_Agreements", active_district, ".csv")))


#Create individual year columns to assign agreements to different years based on start date and duration - code for that to follow below
CS.ng$y.2016 <- 0
CS.ng$y.2017 <- 0 
CS.ng$y.2018 <- 0
CS.ng$y.2019 <- 0
CS.ng$y.2020 <- 0
CS.ng$y.2021 <- 0
CS.ng$y.2022 <- 0
CS.ng$y.2023 <- 0
CS.ng$y.2024 <- 0

#> Get unique combinations of agreements-years
unique.agree2 <- count(CS.ng, STARTDATE.2, Years) %>% 
  ungroup()
#> Export
write_csv(unique.agree2, (here("Out", "AES", "CS", "CS_Unique_Agree-Year_for_checking.csv")))


#> 1. Agreements starting in 2016 running for 10 years
cs.2016.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2016-01-01") & STARTDATE.2 <= as.Date("2016-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2016.10)[1] != 0) {
#> Update relevant cols
cs.2016.10$y.2016 = 1
cs.2016.10$y.2017 = 1
cs.2016.10$y.2018 = 1
cs.2016.10$y.2019 = 1
cs.2016.10$y.2020 = 1
cs.2016.10$y.2021 = 1
cs.2016.10$y.2022 = 1
cs.2016.10$y.2023 = 1
cs.2016.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2016[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2016
CS.ng$y.2017[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2017
CS.ng$y.2018[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2018
CS.ng$y.2019[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2019
CS.ng$y.2020[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2020
CS.ng$y.2021[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2021
CS.ng$y.2022[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2022
CS.ng$y.2023[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2023
CS.ng$y.2024[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2024
}


#> 2. Agreements starting in 2017 running for 10 years
cs.2017.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2017-01-01") & STARTDATE.2 <= as.Date("2017-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2017.10)[1] != 0) {
#> Update relevant cols
cs.2017.10$y.2017 = 1
cs.2017.10$y.2018 = 1
cs.2017.10$y.2019 = 1
cs.2017.10$y.2020 = 1
cs.2017.10$y.2021 = 1
cs.2017.10$y.2022 = 1
cs.2017.10$y.2023 = 1
cs.2017.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2017[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2017
CS.ng$y.2018[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2018
CS.ng$y.2019[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2019
CS.ng$y.2020[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2020
CS.ng$y.2021[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2021
CS.ng$y.2022[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2022
CS.ng$y.2023[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2023
CS.ng$y.2024[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2024
}



#> 3. Agreements starting in 2018 running for 5 years 
cs.2018.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.5)[1] != 0) {
#> Update relevant cols
cs.2018.5$y.2018 = 1
cs.2018.5$y.2019 = 1
cs.2018.5$y.2020 = 1
cs.2018.5$y.2021 = 1
cs.2018.5$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2018
CS.ng$y.2019[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2019
CS.ng$y.2020[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2020
CS.ng$y.2021[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2021
CS.ng$y.2022[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2022
}



#> 4. Agreements starting in 2018 running for 10 years 
cs.2018.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.10)[1] != 0) {
#> Update relevant cols
cs.2018.10$y.2018 = 1
cs.2018.10$y.2019 = 1
cs.2018.10$y.2020 = 1
cs.2018.10$y.2021 = 1
cs.2018.10$y.2022 = 1
cs.2018.10$y.2023 = 1
cs.2018.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2018
CS.ng$y.2019[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2019
CS.ng$y.2020[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2020
CS.ng$y.2021[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2021
CS.ng$y.2022[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2022
CS.ng$y.2023[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2023
CS.ng$y.2024[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2024
}



#> 5. Agreements starting in 2019 running for 5 years 
cs.2019.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.5)[1] != 0) {
#> Update relevant cols
cs.2019.5$y.2019 = 1
cs.2019.5$y.2020 = 1
cs.2019.5$y.2021 = 1
cs.2019.5$y.2022 = 1
cs.2019.5$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2019
CS.ng$y.2020[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2020
CS.ng$y.2021[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2021
CS.ng$y.2022[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2022
CS.ng$y.2023[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2023
}



#> 6. Agreements starting in 2019 running for 10 years 
cs.2019.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.10)[1] != 0) {
#> Update relevant cols
cs.2019.10$y.2019 = 1
cs.2019.10$y.2020 = 1
cs.2019.10$y.2021 = 1
cs.2019.10$y.2022 = 1
cs.2019.10$y.2023 = 1
cs.2019.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2019
CS.ng$y.2020[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2020
CS.ng$y.2021[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2021
CS.ng$y.2022[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2022
CS.ng$y.2023[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2023
CS.ng$y.2024[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2024
}



#> 7. Agreements starting in 20 running for 2years 
cs.2020.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.2)[1] != 0) {
#> Update relevant cols
cs.2020.2$y.2020 = 1
cs.2020.2$y.2021 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2020
CS.ng$y.2021[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2021
}



#> 8. Agreements starting in 20 running for 5 years 
cs.2020.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.5)[1] != 0) {
#> Update relevant cols
cs.2020.5$y.2020 = 1
cs.2020.5$y.2021 = 1
cs.2020.5$y.2022 = 1
cs.2020.5$y.2023 = 1
cs.2020.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2020
CS.ng$y.2021[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2021
CS.ng$y.2022[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2022
CS.ng$y.2023[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2023
CS.ng$y.2024[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2024
}



#> 9. Agreements starting in 20 running for 10 years 
cs.2020.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.10)[1] != 0) {
#> Update relevant cols
cs.2020.10$y.2020 = 1
cs.2020.10$y.2021 = 1
cs.2020.10$y.2022 = 1
cs.2020.10$y.2023 = 1
cs.2020.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2020
CS.ng$y.2021[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2021
CS.ng$y.2022[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2022
CS.ng$y.2023[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2023
CS.ng$y.2024[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2024
}



#> 10. Agreements starting in 21 running for 2 years 
cs.2021.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.2)[1] != 0) {
#> Update relevant cols
cs.2021.2$y.2021 = 1
cs.2021.2$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2021
CS.ng$y.2022[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2022
}


#> 11. Agreements starting in 21 running for 5 years 
cs.2021.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.5 )[1] != 0) {
#> Update relevant cols
cs.2021.5$y.2021 = 1
cs.2021.5$y.2022 = 1
cs.2021.5$y.2023 = 1
cs.2021.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2021
CS.ng$y.2022[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2022
CS.ng$y.2023[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2023
CS.ng$y.2024[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2024
}



#> 11. Agreements starting in 21 running for 10 years 
cs.2021.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.10)[1] != 0) {
#> Update relevant cols
cs.2021.10$y.2021 = 1
cs.2021.10$y.2022 = 1
cs.2021.10$y.2023 = 1
cs.2021.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2021
CS.ng$y.2022[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2022
CS.ng$y.2023[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2023
CS.ng$y.2024[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2024
}



#> 12. Agreements starting in 21 running for 20 years 
cs.2021.20 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 20)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.20 )[1] != 0) {
#> Update relevant cols
cs.2021.20$y.2021 = 1
cs.2021.20$y.2022 = 1
cs.2021.20$y.2023 = 1
cs.2021.20$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2021
CS.ng$y.2022[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2022
CS.ng$y.2023[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2023
CS.ng$y.2024[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2024
}



#> 13. Agreements starting in 22 running for 2 years 
cs.2022.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.2)[1] != 0) {
#> Update relevant cols
cs.2022.2$y.2022 = 1
cs.2022.2$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2022
CS.ng$y.2023[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2023
}



#> 14. Agreements starting in 22 running for 5 years 
cs.2022.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.5)[1] != 0) {
#> Update relevant cols
cs.2022.5$y.2022 = 1
cs.2022.5$y.2023 = 1
cs.2022.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2022
CS.ng$y.2023[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2023
CS.ng$y.2024[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2024
}



#> 15. Agreements starting in 22 running for 10 years 
cs.2022.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.10)[1] != 0) {
#> Update relevant cols
cs.2022.10$y.2022 = 1
cs.2022.10$y.2023 = 1
cs.2022.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2022
CS.ng$y.2023[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2023
CS.ng$y.2024[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2024
}



# Remove records where average annual cost id "unavailable"
CS.final <- CS.ng[!(CS.ng$AVGANNCOST=="*Unavailable"),]



# Export final raw data table
write_csv(CS.final, here("Out", "AES", "CS", "District", "CSV", paste0("CS_", active_district, "_Raw_Processed.csv")))

# # Export final raw data table - TESTING
# write_csv(CS.final, here("Out", "AES", "CS", "County", "CSV", paste0("CS__Raw_Processed_Test.csv")))



# Change annual cost column to numerical
CS.final$AVGANNCOST <- as.numeric(CS.final$AVGANNCOST)
CS.final$AVGANNCOST <- round(CS.final$AVGANNCOST, 2)


#> Calculate annual costs
#> Total for 2018
CS.2018.Total <- CS.final %>% 
  filter(y.2018 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2018 <- sum(CS.2018.Total$AVGANNCOST)

#> Total for 2019
CS.2019.Total <- CS.final %>% 
  filter(y.2019 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2019 <- sum(CS.2019.Total$AVGANNCOST)


#> Total for 2020
CS.2020.Total <- CS.final %>% 
  filter(y.2020 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2020 <- sum(CS.2020.Total$AVGANNCOST)


#> Total for 2021
CS.2021.Total <- CS.final %>% 
  filter(y.2021 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2021 <- sum(CS.2021.Total$AVGANNCOST)

#> Total for 2022
CS.2022.Total <- CS.final %>% 
  filter(y.2022 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2022 <- sum(CS.2022.Total$AVGANNCOST)

#> Total for 2023
CS.2023.Total <- CS.final %>% 
  filter(y.2023 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2023 <- sum(CS.2023.Total$AVGANNCOST)

#> Total for 2024
CS.2024.Total <- CS.final %>% 
  filter(y.2024 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2024 <- sum(CS.2024.Total$AVGANNCOST)


#> Create data frame of annual costs
CS_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals.cs <- c(CS.sum.2018, CS.sum.2019, CS.sum.2020, CS.sum.2021, CS.sum.2022, CS.sum.2023, CS.sum.2024)
#> Insert figure for 2018
df2 <- miscTools::insertRow(CS_Summary, 1, totals.cs)
df2 <- as.data.frame(df2)

#> If there are any negative values in df2, convert these to zero
df2[df2 <0] <- 0

#> Print table district.summary on web page
print(knitr::kable(df2, caption = paste0("Table 4.5.", i , " ", "CS payments - ",  active_district)))

#> Make long
df2.plot <- melt(df2)
#> Extract year from string
names(df2.plot)[1]<-paste("Year")
names(df2.plot)[2]<-paste("Value_cs")
df2.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df2.plot$Year)

# Simple bar chart
plot.cs <- ggplot(df2.plot, aes(x=Year, y=Value_cs)) + 
  geom_bar(stat = "identity", fill="#e38d0b", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Countryside Stewardship payments: ", active_district), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_cs / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white", size = 3.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.cs
print(plot.cs)


#> Export the plot
ggsave(here("Out", "AES", "CS", "District", "Plot", paste0("CS_payments_", active_district, ".png")), width = 7, height = 5)

# #> Export the plot - TESTING
# ggsave(here("Out", "AES", "CS", "County", "Plot", paste0("CS_payments_County_Test.png")), width = 7, height = 5)


#Export table
write_csv(df2, here("Out", "AES", "CS", "District", "CSV", paste0("CS_payments_", active_district, ".csv")))


# #Export table - TESTING
# write_csv(df2, here("Out", "AES", "CS", "County", "CSV", "CS_payments_County_Test.csv"))

}



```



### 4.6 CS - National Parks


National Park-level analysis of Countryside Stewardship (CS) payments. Methods overview to follow. 


```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}


#> Get data
CS <- st_read(here("In", "Shape", "AES", "CS_SouthWest_PoI.shp"), stringsAsFactors = FALSE, quiet = TRUE)

#> Create filter string (get names first!)
nat.parks.list <- c("Exmoor", "Dartmoor")

#> Sequential integer counter (for figure numbers)
i <-0 

#> Initiate loop
for(active_park in nat.parks.list){
  
#> Loop counter (for table caption number)
i <- i+1

#> Select target county (this will be start of loop)
target_park <- nat.parks|> 
  filter(NAME == active_park)


#> Intersect with target county polygon
int <- st_intersection(CS, target_park)

#> Rename intersected data
CS.ng <- int

#> New start date field in date format
CS.ng$STARTDATE.2 <- lubridate::dmy_hms(CS.ng$STARTDATE) 
#> New end date field in date format
CS.ng$ENDDATE.2 <- lubridate::dmy_hms(CS.ng$ENDDATE) 
#> Format dates
CS.ng$STARTDATE.2 <- as.Date(CS.ng$STARTDATE.2, format = "%d/%m/%Y")
CS.ng$ENDDATE.2 <- as.Date(CS.ng$ENDDATE.2, format = "%d/%m/%Y")

#> Create a column to get number of years
CS.ng$Years <- as.numeric(CS.ng$ENDDATE.2 - CS.ng$STARTDATE.2)
CS.ng$Years <- CS.ng$Years /365
CS.ng$Years <- round(CS.ng$Years, 0)
#> List of agreement duration in years - unique duration
years.unique <- unique(CS.ng$Years)

# #> Export table for team use
# write_csv(CS.ng, here("Out", "AES", "CS", "County", "CSV", paste0("CS_Agreements_", active_county, ".csv")))


#> Export table for team use
write_csv(CS.ng, here("Out", "AES", "CS", "Nat_Park", "CSV", paste0("CS_Agreements", active_park, ".csv")))


#Create individual year columns to assign agreements to different years based on start date and duration - code for that to follow below
CS.ng$y.2016 <- 0
CS.ng$y.2017 <- 0 
CS.ng$y.2018 <- 0
CS.ng$y.2019 <- 0
CS.ng$y.2020 <- 0
CS.ng$y.2021 <- 0
CS.ng$y.2022 <- 0
CS.ng$y.2023 <- 0
CS.ng$y.2024 <- 0

#> Get unique combinations of agreements-years
unique.agree2 <- count(CS.ng, STARTDATE.2, Years) %>% 
  ungroup()
#> Export
write_csv(unique.agree2, (here("Out", "AES", "CS", "CS_Unique_Agree-Year_for_checking.csv")))


#> 1. Agreements starting in 2016 running for 10 years
cs.2016.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2016-01-01") & STARTDATE.2 <= as.Date("2016-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2016.10)[1] != 0) {
#> Update relevant cols
cs.2016.10$y.2016 = 1
cs.2016.10$y.2017 = 1
cs.2016.10$y.2018 = 1
cs.2016.10$y.2019 = 1
cs.2016.10$y.2020 = 1
cs.2016.10$y.2021 = 1
cs.2016.10$y.2022 = 1
cs.2016.10$y.2023 = 1
cs.2016.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2016[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2016
CS.ng$y.2017[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2017
CS.ng$y.2018[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2018
CS.ng$y.2019[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2019
CS.ng$y.2020[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2020
CS.ng$y.2021[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2021
CS.ng$y.2022[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2022
CS.ng$y.2023[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2023
CS.ng$y.2024[match(cs.2016.10$CSREF,  CS.ng$CSREF)] <- cs.2016.10$y.2024
}


#> 2. Agreements starting in 2017 running for 10 years
cs.2017.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2017-01-01") & STARTDATE.2 <= as.Date("2017-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2017.10)[1] != 0) {
#> Update relevant cols
cs.2017.10$y.2017 = 1
cs.2017.10$y.2018 = 1
cs.2017.10$y.2019 = 1
cs.2017.10$y.2020 = 1
cs.2017.10$y.2021 = 1
cs.2017.10$y.2022 = 1
cs.2017.10$y.2023 = 1
cs.2017.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2017[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2017
CS.ng$y.2018[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2018
CS.ng$y.2019[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2019
CS.ng$y.2020[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2020
CS.ng$y.2021[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2021
CS.ng$y.2022[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2022
CS.ng$y.2023[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2023
CS.ng$y.2024[match(cs.2017.10$CSREF,  CS.ng$CSREF)] <- cs.2017.10$y.2024
}



#> 3. Agreements starting in 2018 running for 5 years 
cs.2018.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.5)[1] != 0) {
#> Update relevant cols
cs.2018.5$y.2018 = 1
cs.2018.5$y.2019 = 1
cs.2018.5$y.2020 = 1
cs.2018.5$y.2021 = 1
cs.2018.5$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2018
CS.ng$y.2019[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2019
CS.ng$y.2020[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2020
CS.ng$y.2021[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2021
CS.ng$y.2022[match(cs.2018.5$CSREF,  CS.ng$CSREF)] <- cs.2018.5$y.2022
}



#> 4. Agreements starting in 2018 running for 10 years 
cs.2018.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2018-01-01") & STARTDATE.2 <= as.Date("2018-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2018.10)[1] != 0) {
#> Update relevant cols
cs.2018.10$y.2018 = 1
cs.2018.10$y.2019 = 1
cs.2018.10$y.2020 = 1
cs.2018.10$y.2021 = 1
cs.2018.10$y.2022 = 1
cs.2018.10$y.2023 = 1
cs.2018.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2018[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2018
CS.ng$y.2019[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2019
CS.ng$y.2020[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2020
CS.ng$y.2021[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2021
CS.ng$y.2022[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2022
CS.ng$y.2023[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2023
CS.ng$y.2024[match(cs.2018.10$CSREF,  CS.ng$CSREF)] <- cs.2018.10$y.2024
}



#> 5. Agreements starting in 2019 running for 5 years 
cs.2019.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.5)[1] != 0) {
#> Update relevant cols
cs.2019.5$y.2019 = 1
cs.2019.5$y.2020 = 1
cs.2019.5$y.2021 = 1
cs.2019.5$y.2022 = 1
cs.2019.5$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2019
CS.ng$y.2020[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2020
CS.ng$y.2021[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2021
CS.ng$y.2022[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2022
CS.ng$y.2023[match(cs.2019.5$CSREF,  CS.ng$CSREF)] <- cs.2019.5$y.2023
}



#> 6. Agreements starting in 2019 running for 10 years 
cs.2019.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2019-01-01") & STARTDATE.2 <= as.Date("2019-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2019.10)[1] != 0) {
#> Update relevant cols
cs.2019.10$y.2019 = 1
cs.2019.10$y.2020 = 1
cs.2019.10$y.2021 = 1
cs.2019.10$y.2022 = 1
cs.2019.10$y.2023 = 1
cs.2019.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2019[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2019
CS.ng$y.2020[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2020
CS.ng$y.2021[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2021
CS.ng$y.2022[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2022
CS.ng$y.2023[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2023
CS.ng$y.2024[match(cs.2019.10$CSREF,  CS.ng$CSREF)] <- cs.2019.10$y.2024
}



#> 7. Agreements starting in 20 running for 2years 
cs.2020.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.2)[1] != 0) {
#> Update relevant cols
cs.2020.2$y.2020 = 1
cs.2020.2$y.2021 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2020
CS.ng$y.2021[match(cs.2020.2$CSREF,  CS.ng$CSREF)] <- cs.2020.2$y.2021
}



#> 8. Agreements starting in 20 running for 5 years 
cs.2020.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.5)[1] != 0) {
#> Update relevant cols
cs.2020.5$y.2020 = 1
cs.2020.5$y.2021 = 1
cs.2020.5$y.2022 = 1
cs.2020.5$y.2023 = 1
cs.2020.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2020
CS.ng$y.2021[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2021
CS.ng$y.2022[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2022
CS.ng$y.2023[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2023
CS.ng$y.2024[match(cs.2020.5$CSREF,  CS.ng$CSREF)] <- cs.2020.5$y.2024
}



#> 9. Agreements starting in 20 running for 10 years 
cs.2020.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2020-01-01") & STARTDATE.2 <= as.Date("2020-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2020.10)[1] != 0) {
#> Update relevant cols
cs.2020.10$y.2020 = 1
cs.2020.10$y.2021 = 1
cs.2020.10$y.2022 = 1
cs.2020.10$y.2023 = 1
cs.2020.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2020[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2020
CS.ng$y.2021[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2021
CS.ng$y.2022[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2022
CS.ng$y.2023[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2023
CS.ng$y.2024[match(cs.2020.10$CSREF,  CS.ng$CSREF)] <- cs.2020.10$y.2024
}



#> 10. Agreements starting in 21 running for 2 years 
cs.2021.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.2)[1] != 0) {
#> Update relevant cols
cs.2021.2$y.2021 = 1
cs.2021.2$y.2022 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2021
CS.ng$y.2022[match(cs.2021.2$CSREF,  CS.ng$CSREF)] <- cs.2021.2$y.2022
}


#> 11. Agreements starting in 21 running for 5 years 
cs.2021.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.5 )[1] != 0) {
#> Update relevant cols
cs.2021.5$y.2021 = 1
cs.2021.5$y.2022 = 1
cs.2021.5$y.2023 = 1
cs.2021.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2021
CS.ng$y.2022[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2022
CS.ng$y.2023[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2023
CS.ng$y.2024[match(cs.2021.5$CSREF,  CS.ng$CSREF)] <- cs.2021.5$y.2024
}



#> 11. Agreements starting in 21 running for 10 years 
cs.2021.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.10)[1] != 0) {
#> Update relevant cols
cs.2021.10$y.2021 = 1
cs.2021.10$y.2022 = 1
cs.2021.10$y.2023 = 1
cs.2021.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2021
CS.ng$y.2022[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2022
CS.ng$y.2023[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2023
CS.ng$y.2024[match(cs.2021.10$CSREF,  CS.ng$CSREF)] <- cs.2021.10$y.2024
}



#> 12. Agreements starting in 21 running for 20 years 
cs.2021.20 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2021-01-01") & STARTDATE.2 <= as.Date("2021-12-31") & Years == 20)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2021.20 )[1] != 0) {
#> Update relevant cols
cs.2021.20$y.2021 = 1
cs.2021.20$y.2022 = 1
cs.2021.20$y.2023 = 1
cs.2021.20$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2021[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2021
CS.ng$y.2022[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2022
CS.ng$y.2023[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2023
CS.ng$y.2024[match(cs.2021.20$CSREF,  CS.ng$CSREF)] <- cs.2021.20$y.2024
}



#> 13. Agreements starting in 22 running for 2 years 
cs.2022.2 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 2)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.2)[1] != 0) {
#> Update relevant cols
cs.2022.2$y.2022 = 1
cs.2022.2$y.2023 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2022
CS.ng$y.2023[match(cs.2022.2$CSREF,  CS.ng$CSREF)] <- cs.2022.2$y.2023
}



#> 14. Agreements starting in 22 running for 5 years 
cs.2022.5 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 5)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.5)[1] != 0) {
#> Update relevant cols
cs.2022.5$y.2022 = 1
cs.2022.5$y.2023 = 1
cs.2022.5$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2022
CS.ng$y.2023[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2023
CS.ng$y.2024[match(cs.2022.5$CSREF,  CS.ng$CSREF)] <- cs.2022.5$y.2024
}



#> 15. Agreements starting in 22 running for 10 years 
cs.2022.10 <- CS.ng %>%
  select(CSREF, STARTDATE.2, Years, y.2016, y.2017, y.2018, y.2019, y.2020, y.2021, y.2022, y.2023, y.2024) %>% 
  filter(STARTDATE.2 >= as.Date("2022-01-01") & STARTDATE.2 <= as.Date("2022-12-31") & Years == 10)
#> If data frame has no observations skip the subsequent updating of main CS.ng table columns
if (dim(cs.2022.10)[1] != 0) {
#> Update relevant cols
cs.2022.10$y.2022 = 1
cs.2022.10$y.2023 = 1
cs.2022.10$y.2024 = 1
# Update main CS.ng table with data from agreement subset group
CS.ng$y.2022[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2022
CS.ng$y.2023[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2023
CS.ng$y.2024[match(cs.2022.10$CSREF,  CS.ng$CSREF)] <- cs.2022.10$y.2024
}



# Remove records where average annual cost id "unavailable"
CS.final <- CS.ng[!(CS.ng$AVGANNCOST=="*Unavailable"),]



# Export final raw data table
write_csv(CS.final, here("Out", "AES", "CS", "Nat_Park", "CSV", paste0("CS_", active_park, "_Raw_Processed.csv")))

# # Export final raw data table - TESTING
# write_csv(CS.final, here("Out", "AES", "CS", "County", "CSV", paste0("CS__Raw_Processed_Test.csv")))



# Change annual cost column to numerical
CS.final$AVGANNCOST <- as.numeric(CS.final$AVGANNCOST)
CS.final$AVGANNCOST <- round(CS.final$AVGANNCOST, 2)


#> Calculate annual costs
#> Total for 2018
CS.2018.Total <- CS.final %>% 
  filter(y.2018 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2018 <- sum(CS.2018.Total$AVGANNCOST)

#> Total for 2019
CS.2019.Total <- CS.final %>% 
  filter(y.2019 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2019 <- sum(CS.2019.Total$AVGANNCOST)


#> Total for 2020
CS.2020.Total <- CS.final %>% 
  filter(y.2020 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2020 <- sum(CS.2020.Total$AVGANNCOST)


#> Total for 2021
CS.2021.Total <- CS.final %>% 
  filter(y.2021 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2021 <- sum(CS.2021.Total$AVGANNCOST)

#> Total for 2022
CS.2022.Total <- CS.final %>% 
  filter(y.2022 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2022 <- sum(CS.2022.Total$AVGANNCOST)

#> Total for 2023
CS.2023.Total <- CS.final %>% 
  filter(y.2023 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2023 <- sum(CS.2023.Total$AVGANNCOST)

#> Total for 2024
CS.2024.Total <- CS.final %>% 
  filter(y.2024 == 1) %>% 
  select(AVGANNCOST)
#> Variable to hold total sumemd value for year
CS.sum.2024 <- sum(CS.2024.Total$AVGANNCOST)


#> Create data frame of annual costs
CS_Summary <- as.matrix(data.frame(Total_2018 = numeric(0), Total_2019 = numeric(0), Total_2020 = numeric(0), Total_2021 = numeric(0), Total_2022 = numeric(0), Total_2023 = numeric(0), Total_2024 = numeric(0)))
totals.cs <- c(CS.sum.2018, CS.sum.2019, CS.sum.2020, CS.sum.2021, CS.sum.2022, CS.sum.2023, CS.sum.2024)
#> Insert figure for 2018
df2 <- miscTools::insertRow(CS_Summary, 1, totals.cs)
df2 <- as.data.frame(df2)

#> Print table district.summary on web page
print(knitr::kable(df2, caption = paste0("Table 4.6.", i , " ", "CS payments - ",  active_park)))

#> Make long
df2.plot <- melt(df2)
#> Extract year from string
names(df2.plot)[1]<-paste("Year")
names(df2.plot)[2]<-paste("Value_cs")
df2.plot$Year <- sub("^.*([0-9]{4}).*", "\\1", df2.plot$Year)

# Simple bar chart
plot.cs <- ggplot(df2.plot, aes(x=Year, y=Value_cs)) + 
  geom_bar(stat = "identity", fill="#e38d0b", width = 0.6) +
  theme_bw() +
  labs(title = paste0("Countryside Stewardship payments: ", active_park), x = "Year", y = "Value (£)") +
  geom_text(aes(label= paste0(round(Value_cs / 1000000, digits = 2), " M")), vjust = 1.5, colour = "white", size = 3.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16, b = 0, l = 0))) +
  theme(axis.title.x = element_text(margin = margin(t = 12, r = 0, b = 0, l = 0))) +
  theme(legend.position="none") +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
plot.cs
print(plot.cs)


#> Export the plot
ggsave(here("Out", "AES", "CS", "Nat_Park", "Plot", paste0("CS_payments_", active_park, ".png")), width = 7, height = 5)

# #> Export the plot - TESTING
# ggsave(here("Out", "AES", "CS", "County", "Plot", paste0("CS_payments_County_Test.png")), width = 7, height = 5)


#Export table
write_csv(df2, here("Out", "AES", "CS", "Nat_Park", "CSV", paste0("CS_payments_", active_park, ".csv")))


# #Export table - TESTING
# write_csv(df2, here("Out", "AES", "CS", "County", "CSV", "CS_payments_County_Test.csv"))

}



```
<br />


### 4.7 AES Claimant numbers

Calculating the number of AES claimants in each county (February 2022 data - Natural England)

<br />


#### Environmental Stewardship



```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Create a summary table that will be populated by for loop below
ES.claimants <- data.frame(County=as.character(), Claimants=as.numeric())

i <- 0
#> Initiate loop
for(active_county in counties){
  
#> Loop counter (for table caption number)
i <- i+1

#> Get a boundary shapefile for the active county
target_county <- counties.sw |>
  filter(NAME == active_county)

#> Intersect with target county polygon
int <- st_intersection(ES, target_county)

#> Create non-geom version 
ES.ng <- int
st_geometry(ES.ng) <- NULL


df.ES.claim <- ES.ng |> 
  mutate(County = active_county) |> 
  select(County) |> 
  group_by(County) |> 
  summarise(Claimants = n())

#> add total to 
ES.claimants <- rbind(ES.claimants, df.ES.claim)

int <- NULL
df.ES.claim <- NULL

}

#> Print table on web page
print(knitr::kable(ES.claimants, caption = "Table 4.6.1  No. of ES claimants by county"))

#> Export table
write_csv(ES.claimants, here("Out", "Claimants", "CSV", "ES_Claimants_by_County.csv"))


```

<br />
<br />


#### Countryside Stewardship

```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

#> Create a summary table that will be populated by for loop below
CS.claimants <- data.frame(County=as.character(), Claimants=as.numeric())

i <- 0
#> Initiate loop
for(active_county in counties){
  
#> Loop counter (for table caption number)
i <- i+1

#> Get a boundary shapefile for the active county
target_county <- counties.sw |>
  filter(NAME == active_county)

#> Intersect with target county polygon
int <- st_intersection(CS, target_county)

#> Create non-geom version 
CS.ng <- int
st_geometry(CS.ng) <- NULL


df.CS.claim <- CS.ng |> 
  mutate(County = active_county) |> 
  select(County) |> 
  group_by(County) |> 
  summarise(Claimants = n())

#> add total to 
CS.claimants <- rbind(CS.claimants, df.CS.claim)

int <- NULL
df.CS.claim <- NULL

}

#> Print table on web page
print(knitr::kable(CS.claimants, caption = "Table 4.6.2  No. of CS claimants by county"))

#> Export table
write_csv(CS.claimants, here("Out", "Claimants", "CSV", "CS_Claimants_by_County.csv"))


```
































<br />


## 5. Agri land proportions calcs

<br />

Summary of Corine agricultural land cover types (all) by county


```{r echo=TRUE, eval=TRUE, results='asis', fig.height = 6, fig.width = 9}

# #> Get corine agri data (pre-clipped to South West in QGIS
agri.land <- corine.sw
#> Get land class description from lookup
#> Get LUT
corine.LUT <- read_csv(here("In", "Shape", "clc_legend.csv"))
#> Add agri land class desciption based on LUT
agri.land <- merge(agri.land, corine.LUT, by.x = "CODE_18", by.y = "CLC_CODE", all.x = TRUE)
#> Set CRS
agri.land.bng <- st_transform(agri.land, 27700)
#> Intersect by county then calc areas then summarise
int.land <- st_intersection(agri.land.bng, counties.sw)
#> Reduce table
int.land <- int.land |> 
  select(ID, GRID_CODE, Landcover_class, LABEL3, NAME)
#> Area calc
int.land$area <- st_area(int.land)
#> Remove geom
st_geometry(int.land) <- NULL
#> Convert area to KM2
int.land$area <- set_units(int.land$area, km^2)
int.land$area <- round(int.land$area, digits = 3)

#> Group by county and summarise
corine.stats <- int.land |> 
  group_by(NAME, LABEL3) |> 
  summarise(Area_KM2 = sum(area)) |> 
  ungroup() |> 
  mutate(row = row_number()) |> 
  pivot_wider(id_cols = -row, names_from = NAME, values_from = Area_KM2) |> 
  rename(Land_Cover_Type = LABEL3)
#> Change values to numeric
corine.stats[, 2:5] <- lapply(corine.stats[, 2:5], as.numeric)
#> Change NAs to zero
corine.stats[is.na(corine.stats)] <- 0


#> Print table on web page
print(knitr::kable(corine.stats, caption = "Table 5.1 Agricultural land area classes (KM2) by county"))


#Export table
write_csv(corine.stats, here("Out", "Corine", "CSV", "Corine_agri_area_by_county.csv"))



```
